---
title: "NEWS-ContDataQC"
output: github_document
  #md_document:
   # variant: markdown_github
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

Version history.

# v2.0.1
2017-03-06

* Bug fix for variable names not showing up.

* Created environment ContData.env and assigned all variables in fun.UserDefinedValues.R file to it.

* Renamed fun.UserDefinedValues.R to env.UserDefinedValues.R.

* Converted all RMD and R files in package to use ContData.env$.

* Added NEWS.md

* Edited earlier fix to fun.QC.R for adding day, month, year to data.  Did not use variable names in previous edit.

* Create RMD files for ReadMe and NEWS.  Added RMD to ignore list.

# v2.0.0
2017-02-28

* Released on GitHub as a fully documented package.

* Update for TN, Modified QC report (RMD) to summarize number of samples differently.  

* Included tables in Aggregate report (RMD).  

* Reworked scripts to be run as a library.  

* Uploaded to GitHub.

# v1.2.1
2017-01-16

* Update for NJ, fixed date/time issue when resaving files in Excel.  

* Added date/time QC process to be run again at the aggregate step.

# v1.2.0
2016-05-04

* NWQMC 2016, Tampa, FL

# v1.1.0
2016-03-31

* AMAAB 2016, Cacapon, WV

* Minor 

# v1.0.0
2015-10-26

* SWPBA 2015, Myrtle Beach, SC

* Initial public release.