---
title: "ContDataQC Library Creation"
output: html_notebook
---

Helper code for creating library.

Erik.Leppo@tetratech.com
2017-09-26

# Package

Package related code.

## Vignette
```{r, eval=FALSE}
# generate Vignette
library(ContDataQC)
library(devtools)
devtools::build_vignettes()

devtools::use_vignette("ContDataQC_Vignette")
```
devtools::build() more useful and build_vignettes()

## Create Package
Use the code below to create the package.  Assumes you are in the development package directory

```{r, eval=FALSE}
# Library Name
myLibrary <- "ContDataQC"
# Load Library
library(devtools)
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Create Package
# create(myLibrary)
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Document, Install, and Reload Library
## Generate Documentation
setwd(paste0("./",myLibrary))
devtools::document()
## Install New Package (locally)
setwd("..") # return to root directory first
devtools::install(myLibrary)
## Reload library
library(myLibrary,character.only = TRUE)
# change wd back to package
setwd(paste0("./",myLibrary))
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

After creating the package reload it after restarting R within RStudio (Ctrl + Shift + F10).

```{r, eval=FALSE}
# Restart R within RStudio:  Ctrl + Shift + F10
library(ContDataQC)
?CompSiteCDF
??ContDataQC
?fun.Export.IHA
?Export.StreamThermal  
```

## Including Data
All data should have already been created.

## Check

```{r, eval=FALSE}
# Check for errors (or press Cmd + Shift + E in RStudio)
#http://r-pkgs.had.co.nz/check.html
devtools::check()
```

If use RStudio, Build - Check Package, the output is easier to read. 

## Test
Need to use testthat but not to that stage yet.

RStudio, Build - Test Package.


# Other Stuff

```{r, eval=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Upload to Github via GitHub Desktop utility
# 0. download from web via "clone or download" via "Open in Desktop" (GitHub Desktop) if not already in GitHub Desktop
# 1. Make changes in download/clone folder. (done above)
# 3. Open GH Desktop commit changes then sync.
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# install from GitHub (via devtools)
devtools::install_github(paste0("leppott/",myLibrary))
#



#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# remove installed packages (if needed for troubleshooting)
search() # find
#detach(3) # remove by number
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~


# to build package
#https://thepoliticalmethodologist.com/2014/08/14/building-and-maintaining-r-packages-with-devtools-and-roxygen2/
# To build the package as a compressed file in your working directory, run build(current.code, path=getwd()).

# to save internal data for examples
# example
#http://r-pkgs.had.co.nz/data.html#data-sysdata
# have to be at root directory (above package)
#devtools::use_data(NV.predictors,NV.bugs,pkg="MMIcalcNV",internal=TRUE,overwrite=TRUE)
## verify with data()

# To save RMD files
# http://stackoverflow.com/questions/30377213/how-to-include-rmarkdown-file-in-r-package
# /pkg/inst/rmd/
# system.file("rmd/file.Rmd", package="packagename")
#
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#https://hilaryparker.com/2014/04/29/writing-an-r-package-from-scratch/
# Create Package
# create(myLibrary)

```

