---
title: "ContDataQC, Custom Config Files"
author: "Erik W. Leppo"
date: "`r Sys.Date()`"
output: 
rmarkdown::html_vignette:
vignette: >
  %\VignetteIndexEntry{Config_Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction
`ContDataQC` uses a configuration file (config.R) that allows for customization.  Through the use of a configuration file the user can change many of the variables in the library used in the processing of data  (e.g., the names of fields, thresholds, and date formats).

The ContDataQC() function allows the user to input their own configuration file.  Only variables that are different from the default need to be added.  That is, the default configuration is loaded in the library and then the user supplied configuration.  This allows the user configuration to overwrite the defaults for that session.

The Config.out will output the contents of the configuration file as used by the package and stored in the environment ContData.env.

# Viewing Config Setting
The contents of the default configuration file (extdata/config.ORIG.R) can be output with the `Config.Out` function. An HTML (default) or DOCX report is generated along with a text file (.r) of the configuration file.

```{r fun_Config.Out, eval=FALSE}
library(ContDataQC)
Config.Out()

```

# Editing Parameters
The config file that is generated by the `Config.Out` function can be modified to contain the custom values.  Only  modified values need to be included in the custom configuration file.  That is, if you only want to modify a single variable you only need to include this single variable in your custom configuration file.  

This process works because the default configuration is always loaded with the package at start up.  Then any parameters specified in a custom configuration are loaded and overwrite the defaults.

The file can be edited in a text editor or in R-Studio.  It is not recommended to use Word or other word processing programs.

## R Conventions
R code has a few conventions that the user should be aware of when making edits to the configuration file.

* Any text after a "#" is treated as comments and not evaluated.

* The arrow, "<-", is treated as a equal sign when assigning values to a parameter.

* All parameters in the configuration file will be a part of the environment "ContData.env".
    + Thus, all parameters start with "ContData.env$"

## Saving Modified File
A custom configuration file should follow the format of the default configuaration file.  And should be saved as a ".r" file (or ".R").

# Config Contents

The contents of the default configuration file (extdata/config.ORIG.R) are listed below.  Sections are created with similar variables.  Please note that the window below is narrow and some lines wrap to the next line.

```{r Config, comment="", eval=TRUE, echo=FALSE}
fn <- file.path(system.file("extdata", "config.ORIG.R", package="ContDataQC"))
cat(readLines(fn), sep="\n")
```


