---
title: "Overview"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
always_allow_html: true
output:
  html_fragment:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(results='asis', echo=FALSE, warning=FALSE, message = FALSE, fig.align="center")
# needed for trouble shooting
boo_DEBUG <- FALSE
if(boo_DEBUG==TRUE){
  # myConfig <- file.path(system.file(package="ContDataQC"), "extdata", "config.ORIG.R")
  # source(myConfig)
}## IF ~ boo_DEBUG ~ END
```

# Overview

The ContDataQC Shiny app is a free R-based tool to QC, combine, and summarize continuous data files in a standardized way without having to download any programs to your computer. It also has a function that allows users to download USGS gage data for desired time periods. The table at the bottom of this page shows how the website is structured.

To date, ContDataQC has been used primarily on continuous temperature and hydrologic data but can also be used for conductivity, pH, turbidity and chlorophyll-a. Users can add other parameters as well but this requires more advanced R skills.

This Shiny app is linked to the ContDataQC R package, which was developed by Erik W. Leppo from Tetra Tech (Erik.Leppo@tetratech.com) and is available on [GitHub](https://github.com/leppott/ContDataQC).

Development of the ContDataQC R tools has been funded by the United States Environmental Protection Agency (EPA) Office of Research and Development (ORD) as part of a larger project to establish Regional Monitoring Networks (RMNs) for freshwater streams and inland lakes (USEPA 2016, USEPA 2021; lead EPA scientist: Britta Bierwagen). The RMNs are a volunteer, collaborative effort in which entities collect long-term continuous temperature and hydrologic data at targeted sites to detect changes over time. The R package and Shiny app were developed with the following objectives in mind: ensure that a certain (minimum) level of QC is being performed on the continuous RMN data; standardize and speed up data QC and reduce missed errors; standardize data for further analysis; and facilitate data sharing.


### Guide to the ContDataQC R Shiny app
```{r table_1}
library(readxl)
library(knitr)
library(kableExtra)
# state directories
table.dir <- "tables"
table.file <- "App_Information_Tables.xlsx"
tab1.dir <- "Overview_Table1"

table1 <- read_excel(file.path(table.dir, table.file), sheet = tab1.dir
                     , na = c("NA", ""), trim_ws = TRUE, skip = 0
                     , col_names = TRUE)  

options(knitr.kable.NA = '')
# kable(table1)
table1 %>% 
  kbl() %>% 
  kable_styling(full_width = F, position = "left")
```
