---
title: "Main Functions 4a"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
always_allow_html: true
output:
  html_fragment:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(results='asis', echo=FALSE, warning=FALSE, message = FALSE)
# needed for trouble shooting
boo_DEBUG <- FALSE
if(boo_DEBUG==TRUE){
  # myConfig <- file.path(system.file(package="ContDataQC"), "extdata", "config.ORIG.R")
  # source(myConfig)
}## IF ~ boo_DEBUG ~ END
```

# Run Functions

The three main functions are listed in the drop-down menu under ‘Choose Operation to perform’

* **‘QC raw data’** generates QC reports.
* **‘Aggregate QC’d data’** merges the QC'd data files for the desired time periods together. The input files need to be from the same site and share common parameters.
* **‘Summary statistics’** generates two sets of CSV files and a PDF with time series plots for each parameter. One of the CSVs has daily means and the other has a wider range of summary statistics (e.g., min, median, max, quartiles).

ContDataQC works sequentially, meaning the user needs to run the QC function before running the Aggregate function, and the Aggregate function before the SummaryStats function. More detailed information on each function can be found below. 

This video provides an overview of the workflow: **will send link later**

Click **here** to download a PDF with instructions on how to set up Google Chrome so that it asks you where to save each file before downloading (which can be a big time-saver).

### QC reports
Shiny app instructions

1. Click the ‘Browse’ button and select the input file(s) from the Data1_RAW folder. You can run multiple files at once. The status bar will tell you when the upload is complete. 
2. Select ‘QC Raw Data’ from the ‘Choose Operation to perform’ drop-down menu
3. A ‘Run operation’ button will appear. Click this button. A status bar will appear in the lower right corner.
4. After the function is done running, a ‘Download’ button will appear. Click this button.
5. Save the zipped file in the Data2_QC folder.
6. Open the QC reports. There are two types of outputs: a Data Quality Control Report that comes as either a Word document or Hypertext Markup Language (HTML) (the user specifies the desired format); and a comma-delimited (.csv) spreadsheet. The reports include results from the ‘flag’ tests (gross, spike, rate of change and flat line), missing data checks and time series plots.
7. Review each set of files, check flagged data points, do visual checks on the time series plots, and decide if and how to make corrections.

The Data Quality Control Report is organized into four main sections, starting with an overall summary followed by summaries for each parameter:

1. Data file information (siteID, date range, parameters, recording interval, QC test thresholds reference table)
2. ‘Count’ tables (# measurements/day) so that you can find inconsistencies (too few measurements (=missing data) or too many measurements)
3. Results from the four ‘flag’ tests (gross, spike, rate of change and flat line) - # of entries marked as pass (P), suspect (S), fail (F), missing data (X) or not available (NA)
4. Time series plots for each individual parameter and two sets of combined parameters (water and air temperature; water temperature and water level). It can also plot discrete/in situ values taken during site visits for accuracy checks (the discrete data points are overlaid on top of the sensor data). These are in situ measurements taken when people do field work and are used for calibration/validation of these continuous sensors

TEMPLATE 
[here](PUT HYPERLINK HERE).

## Subheading

Bullets:

* Bullet 1
* Bullet 2

### Table 1. Table Name.
```{r table_1}
library(readxl)
library(knitr)
library(kableExtra)
# state directories
table.dir <- "tables"
table.file <- "Instruction_Tables.xlsx"
tab1.dir <- "Instr_table2"

table1 <- read_excel(file.path(table.dir, table.file), sheet = tab1.dir
                     , na = c("NA", ""), trim_ws = TRUE, skip = 0
                     , col_names = TRUE)  

# kable(table1)
table1 %>% 
  kbl() %>% 
  kable_styling(full_width = F, position = "left")
```

