---
title: "3a Organizing Data"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
always_allow_html: true
output:
  html_fragment:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(results = 'asis', echo = FALSE, warning = FALSE, message = FALSE)
# needed for trouble shooting
boo_DEBUG <- FALSE
if (boo_DEBUG == TRUE) {
  # myConfig <- file.path(system.file(package="ContDataQC"), "extdata", "config.ORIG.R")
  # source(myConfig)
}## IF ~ boo_DEBUG ~ END
```

# Organizing Files

If you do not already have a good system for organizing continuous data files, we recommend that you set up a folder for each site, and within each site folder, set up subfolders as shown in the table below. You can download a ready-made set of (empty) folders by clicking [here](SiteX_20230828.zip) [ZIP]. Put the file in the desired location, unzip it and then replace ‘SiteX’ with the appropriate site name.

You have more flexibility with file organization when using the Shiny app vs R package. With the Shiny app, it is not necessary to name the folders exactly as shown below because you can browse to the desired input files and browse to save the output files to the desired location. However, if you decide to use the R package at some point, keeping the four ‘Data’ folders (Data0_Original, Data1_RAW, Data2_QC, Data3_Aggregated and Data4_Stats) will be important since the R code searches in specific folders for input files and outputs files to specific directories. Advanced users can modify the default directories by editing the configuration file.


### Folder descriptions
```{r table_1}
library(readxl)
library(knitr)
library(kableExtra)
# state directories
table.dir <- "tables"
table.file <- "App_Information_Tables.xlsx"
tab2a.dir <- "DataPrep_Table2a"

table2a <- read_excel(file.path(table.dir, table.file), sheet = tab2a.dir
                     , na = c("NA", ""), trim_ws = TRUE, skip = 0
                     , col_names = TRUE)  

options(knitr.kable.NA = '')
# kable(table1)
table2a %>% 
  kbl() %>% 
  kable_styling(full_width = F, position = "left")
```