---
title: "DataPrep_miniDOT_Reformat, 3f"
output: html_fragment
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
# ---
# title: "DataPrep_miniDOT_Reformat"
# date: '2022-06-01'
# ---
knitr::opts_chunk$set(echo = FALSE)
```

# miniDOT DO Reformat

After the daily files are concatenated, run the combined file through
the Reformat function. The function reformats the file so that it is
ready to run through the QC report function.

## Instructions

-   Click the 'Browse' button and select the input file(s). You can run
    multiple files at once. The status bar will tell you when the upload
    is complete.

-   Click the 'Reformat miniDOT file(s)' button; a status bar will
    appear in the lower right corner.

-   After the function is done running, a 'Download' button will appear.
    Click this button.

-   You will be prompted to save a zipped file named
    'miniDOT_reformat_date_time'. Save the zipped file in the Data1_RAW
    folder.

-   Unzip/extract the file(s) or else the files won't be seen as an
    option to upload to the QC report function (Main Functions - QC raw
    data). After file is unzipped, a new folder called
    'miniDOT_reformat' will appear. The original zipped file can be
    deleted if desired.

-   See below for examples of files before and after reformatting.

## Additional Notes

-   Want to try it yourself? Click [here](TestData_miniDOT.zip) [ZIP] to
    download miniDOT DO test files.

*	Why are the DO saturation values all NA? This occurs when no inputs are 
provided to calculate DO percent saturation.  For more information, please see 
miniDOT manual or contact the miniDOT support team.

## Example

Example table before after performing the **Reformat** function.

**Before**

```{r}
library(readxl)
library(knitr)
library(kableExtra)
# state directories
table.dir  <- "tables"
table.file <- "miniDOTreformat_ BEFORE_20240131.xlsx"
table.sheet  <- "Sheet1"

table <- read_excel(file.path(table.dir, table.file), sheet = table.sheet
                     , na = c("NA", ""), trim_ws = TRUE, skip = 0
                     , col_names = TRUE)  

options(knitr.kable.NA = '')
# kable(table1)
table %>% 
  kbl() %>% 
  kable_styling(full_width = F, position = "left")

cat("\n\n")
```

**After**

```{r}
library(readxl)
library(knitr)
library(kableExtra)
# state directories
table.dir  <- "tables"
table.file <- "miniDOTreformat_ AFTER_20240131.xlsx"
table.sheet  <- "Sheet1"

table <- read_excel(file.path(table.dir, table.file), sheet = table.sheet
                     , na = c("NA", ""), trim_ws = TRUE, skip = 0
                     , col_names = TRUE)  

options(knitr.kable.NA = '')
# kable(table1)
table %>% 
  kbl() %>% 
  kable_styling(full_width = F, position = "left")
```

