---
title: "QC Thresholds 4c"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
always_allow_html: true
output:
  html_fragment:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(results='asis', echo=FALSE, warning=FALSE, message = FALSE)
# needed for trouble shooting
boo_DEBUG <- FALSE
if(boo_DEBUG==TRUE){
  # myConfig <- file.path(system.file(package="ContDataQC"), "extdata", "config.ORIG.R")
  # source(myConfig)
}## IF ~ boo_DEBUG ~ END
```

## Edit Thresholds

Click [here](EditingQCtestThresholds_20220117.pdf) [PDF] for instructions on how to 
edit thresholds and create customized configuration files. There are two options
(see below). For either option, save the customized configuration file in a 
folder that is easy to find so that you can reuse the file each time you QC data
for that site. It is helpful to include the StationID and other relevant 
information in the file name (for example, if thresholds are customized for a 
particular season). 

After you save the file, go to the 'upload custom thresholds' tab, browse to the
custom thresholds file, upload the file and then, under 'Run functions', 
generate the QC reports. If you forget the upload step, the default QC 
thresholds will be used.

### Option 1, download the default configuration file, open the file in R or Notepad++, make edits and save.

Configuration files can be downloaded here -

*	[Default](Config_default.zip) [ZIP], with hydrologic parameters in feet.

*	[Hydrologic parameters in meters](Config_Lakes_meters.zip) [ZIP].

Navigate to the ‘QC tests and calculations’ section of the configuration file, which is about halfway through the file. Edit thresholds as desired. Save the file.

When you download the configuration file(s), you will see two types of files: an
R file (.R) and a text (.txt) file for users who do not have R installed on 
their computer. You can download R from this website: 
<a href="https://cran.r-project.org" data-once="external-links protected-links" target="_blank">https://cran.r-project.org<svg class="icon icon--exit is-spaced-before" role="img"> == $0 <title>Exit EPA's website</title><use href="https://www.epa.gov/themes/epa_theme/images/sprite.svg#launch"></use></svg></a>. 
You may also want to download 
<a href="https://www.rstudio.com/products/rstudio/download/" data-once="external-links protected-links" target="_blank">RStudio<svg class="icon icon--exit is-spaced-before" role="img"> == $0 <title>Exit EPA's website</title><use href="https://www.epa.gov/themes/epa_theme/images/sprite.svg#launch"></use></svg></a>,
which is a separate program but is a useful code editor and interface (IDE) for 
R. If you cannot install R on your computer, we recommend use Notepad or 
<a href="https://notepad-plus-plus.org/downloads" data-once="external-links protected-links" target="_blank">Notepad++<svg class="icon icon--exit is-spaced-before" role="img"> == $0 <title>Exit EPA's website</title><use href="https://www.epa.gov/themes/epa_theme/images/sprite.svg#launch"></use></svg></a>
(some people prefer Notepad++ because it has color-coding).


### Option 2, use the interactive functions.

* Select a parameter using the drop-down menu (upper left box)

* Edit thresholds using the boxes below

* After you make changes for each parameter, click ‘save changes’ as you go (upper left box). Otherwise when you switch to a different parameter, it won’t save the changes you made to the previous parameter. 

* Download custom thresholds file

```{r}
Parameter <- c("Temperature"
              , "Sensor depth and water level"
              , "Discharge"
              , "Dissolved oxygen"
              , "DO pctsat"
              , "Conductivity"
              , "Pressure"
              , "pH"
              , "Turbidity"
              , "Salinity"
              , "Chlorophylla")
Units <- c("Celsius"
          , "feet"
          , "ft3/s"
          , "mg/L"
          , "%"
          , "uS/cm"
          , "psi"
          , "SU"
          , "NTU"
          , "ppt"
          , "g/cm3")
df_param_units <- data.frame(Parameter, Units)
cap_param_units <- "Default Units"
knitr::kable(df_param_units, caption = cap_param_units)
```

If you do not want to use the default units, you will need to use Option 1.

Acknowledgment: Tim Martin (MN DNR) wrote the R code that we used for the 
interactive functions below.
