---
title: "QC Thresholds 3a"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
always_allow_html: true
output:
  html_fragment:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(results='asis', echo=FALSE, warning=FALSE, message = FALSE)
# needed for trouble shooting
boo_DEBUG <- FALSE
if(boo_DEBUG==TRUE){
  # myConfig <- file.path(system.file(package="ContDataQC"), "extdata", "config.ORIG.R")
  # source(myConfig)
}## IF ~ boo_DEBUG ~ END
```

# Default QC flag test thresholds

If a customized configuration file is not uploaded prior to running the QC function, the default thresholds and units listed below will be used for the four QC flag tests.

The QC function runs each data point in the input file through the following four 'flag' tests.

### Flag test descriptions

```{r table_1}
library(readxl)
library(knitr)
library(kableExtra)
# state directories
table.dir <- "tables"
table.file <- "App_Information_Tables.xlsx"
tab3a1.dir <- "QCThresh_Table3a1"

table3a1 <- read_excel(file.path(table.dir, table.file), sheet = tab3a1.dir
                     , na = c("NA", ""), trim_ws = TRUE, skip = 0
                     , col_names = TRUE)  

options(knitr.kable.NA = '')
# kable(table1)
table3a1 %>% 
  kbl() %>% 
  kable_styling(full_width = F, position = "left")
```

The 'flag' tests were selected based on the following references:

-   U.S. Integrated Ocean Observing System, 2017. Manual for the Use of Real-Time Oceanographic Data Quality Control Flags, Version 1.1. 43 pp.
<a href="https://cdn.ioos.noaa.gov/media/2017/12/QARTOD-Data-Flags-Manual_Final_version1.1.pdf" target="_blank">https://cdn.ioos.noaa.gov/media/2017/12/QARTOD-Data-Flags-Manual_Final_version1.1.pdf</a>

-   Wagner, R.J., Boulger, R.W., Oblinger, C.J., Smith, B.A., 2006. Guidelines and Standard Procedures for Continuous Water-quality Monitors: Station Operation, Record Computation, and Data Reporting. U.S. Geological Survey Techniques and Methods 1-D3, 51 pp. þ 8 attachments. 
<a href="http://pubs.water.usgs.gov/tm1d3" target="_blank">http://pubs.water.usgs.gov/tm1d3</a>.

R assigns the following flags to each data point:

-   P = Pass

-   S = Suspect

-   F = Fail

-   X = No Data or Not Applicable (NA)

The default thresholds for temperature are based on data from cool, freshwater, wadeable, medium to high gradient streams in the eastern US. Default thresholds for the hydrologic parameters, turbidity and chlorophyll-a are set very high since values vary widely depending on site-specific factors such as stream size. Once you have one or more years of continuous data at a site, we strongly encourage you to evaluate the performance of the QC test thresholds for each parameter and customize the thresholds as needed by editing the configuration file. For more information, see the 'Upload Custom Thresholds' tab.

Units are an important consideration as well. The default configuration puts hydrologic parameters (like water level) in feet, which is generally preferred for streams among RMN partners. However, with lakes, more people prefer meters. If units are changed from feet to meters but there is not a corresponding change in thresholds, the QC tests lose relevance.

Configuration files can be downloaded here: 

-   [Default](Config_default.zip), with hydrologic parameters in feet

-   [Customized](Config_Lakes_meters.zip), with hydrologic parameters in meters

This table shows the default QC test thresholds for each parameter as of 2023-08-28.

### Default QC test thresholds

```{r table_2}
library(readxl)
library(knitr)
library(kableExtra)
# state directories
table.dir <- "tables"
table.file <- "App_Information_Tables.xlsx"
tab3a2.dir <- "QCThresh_Table3a2"

table3a2 <- read_excel(file.path(table.dir, table.file), sheet = tab3a2.dir
                     , na = c("NA", ""), trim_ws = TRUE, skip = 0
                     , col_names = TRUE)  

# kable(table2)
table3a2 %>% 
  kbl() %>% 
  kable_styling(full_width = F, position = "left")
```
