---
title: "Overview"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
always_allow_html: true
output:
  html_fragment:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(results='asis', echo=FALSE, warning=FALSE, message = FALSE, fig.align="center")
# needed for trouble shooting
boo_DEBUG <- FALSE
if(boo_DEBUG==TRUE){
  # myConfig <- file.path(system.file(package="ContDataQC"), "extdata", "config.ORIG.R")
  # source(myConfig)
}## IF ~ boo_DEBUG ~ END
```

# About ContDataQC

The ContDataQC Shiny app is a free R-based tool that was developed to help water quality monitoring programs quality control (QC), merge and summarize continuous sensor data files in a standardized, more efficient way. It also has a function that allows users to download U.S. Geological Survey gage data at sites and over periods of their choosing. This Shiny app is linked to the ContDataQC R package, which was developed for EPA by Tetra Tech in support of the EPA and is 
available on <a class="menu__link" href="https://github.com/USEPA/ContDataQC" target="_blank">GitHub<span class="usa-tag external-link__tag" title="Exit EPA Website">
                    <span aria-hidden="true">Exit</span>
                    <span class="u-visually-hidden"> Exit EPA Website</span>
                  </span>
                </a>.

The ContDataQC R package and Shiny app were developed with the following objectives in mind: ensure that a certain (minimum) level of QC is being performed on continuous data files; standardize and speed up data QC and reduce missed errors; and standardize data for further analysis and sharing. ContDataQC is currently configured for temperature, water level, discharge, conductivity, dissolved oxygen (DO), pH, turbidity, chlorophyll-a and salinity data. Users with advanced R skills can add any other parameters that they desire by making edits to the configuration file, which can be viewed in R or in Notepad.

# ContDataQC Shiny App Workflow

The table below lays out the general workflow for using the ContDataQC app.

```{r}
library(readxl)
library(knitr)
library(kableExtra)
# state directories
table.dir  <- "tables"
table.file <- "App_Information_Tables.xlsx"
table.sheet  <- "About_Overview"

table <- read_excel(file.path(table.dir, table.file), sheet = table.sheet
                     , na = c("NA", ""), trim_ws = TRUE, skip = 0
                     , col_names = TRUE)  

options(knitr.kable.NA = '')
# kable(table1)
table %>% 
  kbl() %>% 
  kable_styling(full_width = F, position = "left")
```

# Funding

Development of the ContDataQC R Shiny app has been funded by the United States 
Environmental Protection Agency (EPA) Office of Research and Development (ORD) as part of a larger project to establish Regional Monitoring Networks (RMNs) for freshwater streams and inland lakes. The RMNs are a volunteer, collaborative effort in which entities collect long-term continuous temperature and hydrologic data at targeted sites to detect changes 
over time. For more information on the RMNs, please refer to the 
<a class="menu__link" href="https://assessments.epa.gov/global/document/&deid=307973" target="_blank">Regional Monitoring Networks (RMN) to Detect Changing Baselines in Freshwater Wadeable Streams (Final Report)</a>.

```{r}

# Removed this from the end of directly above because it is not an external link
# <span class="usa-tag external-link__tag" title="Exit EPA Website">
#                     <span aria-hidden="true">Exit</span>
#                     <span class="u-visually-hidden"> Exit EPA Website</span>
#                   </span>
#                 </a>.
```

# Disclaimer

[NOTICE] The ContDataQC application has not yet received final approval by EPA, a formal peer review is pending. Be advised that any text, figures, or data provided here do not necessarily reflect the views or policies of the EPA.
