---
title: "Report, Configuration"
subtitle: "ContDataQC"
author: "`r Sys.getenv('USERNAME')`"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: no
  word_document:
    toc: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(results='asis', echo=FALSE, warning=FALSE)
# needed for trouble shooting
myConfig <- file.path(system.file(package="ContDataQC"), "extdata", "config.ORIG.R")
#source(myConfig)
```

# FILE INFORMATION
```{r data_file_info}
  # Report Info
  myReportDate <- format(Sys.Date(), ContData.env$myFormat.Date)
  cat(paste("**Report Date:** ",myReportDate,"\n\n",sep=""))
  myUser <- Sys.getenv("USERNAME")
  cat(paste("**Generated By:** ",myUser,"\n\n",sep=""))
  
  #file name
  cat("**File Name:** ",basename(myConfig),"\n\n",sep="")
  #dir name
  cat("**File Location:** ",dirname(myConfig),"\n\n",sep="")

  # Last Modified Date
  cat("**Last Modified:** ",format(file.info(myConfig)$mtime, ContData.env$myFormat.DateTime),"\n\n",sep="")
 
```

# CONFIGURATION SETTINGS
Output of configuration file used in the `ContDataQC` package.

## Thresholds
Table of most relevant thresholds in report ready format.  This is the same table that appears in the QC Report.  The four test types are column headers.

```{r Thresholds}
kbl_caption <- "Thresholds, Quick Reference"
txt_header <- c("Analyte", "Flag", "Gross", "Spike", "Rate of Change", "Flat Line")
# WaterTemp
nam_WaterTemp <- c("myLab.WaterTemp"                        #1
                   , "myUnits.WaterTemp"                    #2
                   , "myThresh.Gross.Fail.Hi.WaterTemp"     #3
                   , "myThresh.Gross.Fail.Lo.WaterTemp"     #4
                   , "myThresh.Gross.Suspect.Hi.WaterTemp"  #5
                   , "myThresh.Gross.Suspect.Lo.WaterTemp"  #6
                   , "myThresh.Spike.Hi.WaterTemp"          #7
                   , "myThresh.Spike.Lo.WaterTemp"          #8
                   , "myThresh.RoC.SD.number.WaterTemp"     #9
                   , "myThresh.RoC.SD.period.WaterTemp"     #10
                   , "myThresh.Flat.Hi.WaterTemp"           #11
                   , "myThresh.Flat.Lo.WaterTemp"           #12
                   , "myThresh.Flat.Tolerance.WaterTemp"    #13
                   )
val_WaterTemp <- mget(nam_WaterTemp, envir=ContData.env)
txt_WaterTemp_F <- c(val_WaterTemp[1]
                     , "Fail"
                     , paste0("> ",val_WaterTemp[3]," deg ",val_WaterTemp[2]
                              ,"  or < ",val_WaterTemp[4]," deg ",val_WaterTemp[2])
                     , paste0(">= ", val_WaterTemp[7]," deg ",val_WaterTemp[2]," (+/-)")
                     , "NA"
                     , paste0("> ",val_WaterTemp[11]
                              ," consecutive measurements within ",val_WaterTemp[13]
                              ," units of one another"))
txt_WaterTemp_S <- c(val_WaterTemp[1]
                     , "Suspect"
                     , paste0("> ",val_WaterTemp[5]," deg ",val_WaterTemp[2]
                              ," or < ",val_WaterTemp[6]," deg ",val_WaterTemp[2])
                     , paste0(">= ", val_WaterTemp[8]," deg ",val_WaterTemp[2]," (+/-)")
                     , paste0(">= ",val_WaterTemp[9]," standard deviations within "
                              ,val_WaterTemp[10]," hours")
                     , paste0("> ",val_WaterTemp[12]
                              ," consecutive measurements within ",val_WaterTemp[13]
                              ," units of one another"))
# AirTemp
nam_AirTemp <- c("myLab.AirTemp"                          #1
                   , "myUnits.AirTemp"                    #2
                   , "myThresh.Gross.Fail.Hi.AirTemp"     #3
                   , "myThresh.Gross.Fail.Lo.AirTemp"     #4
                   , "myThresh.Gross.Suspect.Hi.AirTemp"  #5
                   , "myThresh.Gross.Suspect.Lo.AirTemp"  #6
                   , "myThresh.Spike.Hi.AirTemp"          #7
                   , "myThresh.Spike.Lo.AirTemp"          #8
                   , "myThresh.RoC.SD.number.AirTemp"     #9
                   , "myThresh.RoC.SD.period.AirTemp"     #10
                   , "myThresh.Flat.Hi.AirTemp"           #11
                   , "myThresh.Flat.Lo.AirTemp"           #12
                   , "myThresh.Flat.Tolerance.AirTemp"    #13
                   )
val_AirTemp <- mget(nam_AirTemp, envir=ContData.env)
txt_AirTemp_F <- c(val_AirTemp[1]
                     , "Fail"
                     , paste0("> ",val_AirTemp[3]," deg ",val_AirTemp[2]
                              ,"  or < ",val_AirTemp[4]," deg ",val_AirTemp[2])
                     , paste0(">= ", val_AirTemp[7]," deg ",val_AirTemp[2]," (+/-)")
                     , "NA"
                     , paste0("> ",val_AirTemp[11]
                              ," consecutive measurements within ",val_AirTemp[13]
                              ," units of one another"))
txt_AirTemp_S <- c(val_AirTemp[1]
                     , "Suspect"
                     , paste0("> ",val_AirTemp[5]," deg ",val_AirTemp[2]
                              ," or < ",val_AirTemp[6]," deg ",val_AirTemp[2])
                     , paste0(">= ", val_AirTemp[8]," deg ",val_AirTemp[2]," (+/-)")
                     , paste0(">= ",val_AirTemp[9]," standard deviations within "
                              ,val_AirTemp[10]," hours")
                     , paste0("> ",val_AirTemp[12]
                              ," consecutive measurements within ",val_AirTemp[13]
                              ," units of one another"))
# WaterP
nam_WaterP <- c("myLab.WaterP"                           #1
                   , "myUnits.WaterP"                    #2
                   , "myThresh.Gross.Fail.Hi.WaterP"     #3
                   , "myThresh.Gross.Fail.Lo.WaterP"     #4
                   , "myThresh.Gross.Suspect.Hi.WaterP"  #5
                   , "myThresh.Gross.Suspect.Lo.WaterP"  #6
                   , "myThresh.Spike.Hi.WaterP"          #7
                   , "myThresh.Spike.Lo.WaterP"          #8
                   , "myThresh.RoC.SD.number.WaterP"     #9
                   , "myThresh.RoC.SD.period.WaterP"     #10
                   , "myThresh.Flat.Hi.WaterP"           #11
                   , "myThresh.Flat.Lo.WaterP"           #12
                   , "myThresh.Flat.Tolerance.WaterP"    #13
                   )
val_WaterP <- mget(nam_WaterP, envir=ContData.env)
txt_WaterP_F <- c(val_WaterP[1]
                     , "Fail"
                     , paste0("> ",val_WaterP[3]," ",val_WaterP[2]
                              ,"  or < ",val_WaterP[4]," ",val_WaterP[2])
                     , paste0(">= ", val_WaterP[7]," ",val_WaterP[2]," (+/-)")
                     , "NA"
                     , paste0("> ",val_WaterP[11]
                              ," consecutive measurements within ",val_WaterP[13]
                              ," units of one another"))
txt_WaterP_S <- c(val_WaterP[1]
                     , "Suspect"
                     , paste0("> ",val_WaterP[5]," ",val_WaterP[2]
                              ," or < ",val_WaterP[6]," ",val_WaterP[2])
                     , paste0(">= ", val_WaterP[8]," ",val_WaterP[2]," (+/-)")
                     , paste0(">= ",val_WaterP[9]," standard deviations within "
                              ,val_WaterP[10]," hours")
                     , paste0("> ",val_WaterP[12]
                              ," consecutive measurements within ",val_WaterP[13]
                              ," units of one another"))
# AirBP
nam_AirBP <- c("myLab.AirBP"                            #1
                   , "myUnits.AirBP"                    #2
                   , "myThresh.Gross.Fail.Hi.AirBP"     #3
                   , "myThresh.Gross.Fail.Lo.AirBP"     #4
                   , "myThresh.Gross.Suspect.Hi.AirBP"  #5
                   , "myThresh.Gross.Suspect.Lo.AirBP"  #6
                   , "myThresh.Spike.Hi.AirBP"          #7
                   , "myThresh.Spike.Lo.AirBP"          #8
                   , "myThresh.RoC.SD.number.AirBP"     #9
                   , "myThresh.RoC.SD.period.AirBP"     #10
                   , "myThresh.Flat.Hi.AirBP"           #11
                   , "myThresh.Flat.Lo.AirBP"           #12
                   , "myThresh.Flat.Tolerance.AirBP"    #13
                   )
val_AirBP <- mget(nam_AirBP, envir=ContData.env)
txt_AirBP_F <- c(val_AirBP[1]
                     , "Fail"
                     , paste0("> ",val_AirBP[3]," ",val_AirBP[2]
                              ,"  or < ",val_AirBP[4]," ",val_AirBP[2])
                     , paste0(">= ", val_AirBP[7]," ",val_AirBP[2]," (+/-)")
                     , "NA"
                     , paste0("> ",val_AirBP[11]
                              ," consecutive measurements within ",val_AirBP[13]
                              ," units of one another"))
txt_AirBP_S <- c(val_AirBP[1]
                     , "Suspect"
                     , paste0("> ",val_AirBP[5]," ",val_AirBP[2]
                              ," or < ",val_AirBP[6]," ",val_AirBP[2])
                     , paste0(">= ", val_AirBP[8]," ",val_AirBP[2]," (+/-)")
                     , paste0(">= ",val_AirBP[9]," standard deviations within "
                              ,val_AirBP[10]," hours")
                     , paste0("> ",val_AirBP[12]
                              ," consecutive measurements within ",val_AirBP[13]
                              ," units of one another"))
# SensorDepth
nam_SensorDepth <- c("myLab.SensorDepth"                      #1
                   , "myUnits.SensorDepth"                    #2
                   , "myThresh.Gross.Fail.Hi.SensorDepth"     #3
                   , "myThresh.Gross.Fail.Lo.SensorDepth"     #4
                   , "myThresh.Gross.Suspect.Hi.SensorDepth"  #5
                   , "myThresh.Gross.Suspect.Lo.SensorDepth"  #6
                   , "myThresh.Spike.Hi.SensorDepth"          #7
                   , "myThresh.Spike.Lo.SensorDepth"          #8
                   , "myThresh.RoC.SD.number.SensorDepth"     #9
                   , "myThresh.RoC.SD.period.SensorDepth"     #10
                   , "myThresh.Flat.Hi.SensorDepth"           #11
                   , "myThresh.Flat.Lo.SensorDepth"           #12
                   , "myThresh.Flat.Tolerance.SensorDepth"    #13
                   )
val_SensorDepth <- mget(nam_SensorDepth, envir=ContData.env)
txt_SensorDepth_F <- c(val_SensorDepth[1]
                     , "Fail"
                     , paste0("> ",val_SensorDepth[3]," ",val_SensorDepth[2]
                              ,"  or < ",val_SensorDepth[4]," ",val_SensorDepth[2])
                     , paste0(">= ", val_SensorDepth[7]," ",val_SensorDepth[2]," (+/-)")
                     , "NA"
                     , paste0("> ",val_SensorDepth[11]
                              ," consecutive measurements within ",val_SensorDepth[13]
                              ," units of one another"))
txt_SensorDepth_S <- c(val_SensorDepth[1]
                     , "Suspect"
                     , paste0("> ",val_SensorDepth[5]," ",val_SensorDepth[2]
                              ," or < ",val_SensorDepth[6]," ",val_SensorDepth[2])
                     , paste0(">= ", val_SensorDepth[8]," ",val_SensorDepth[2]," (+/-)")
                     , paste0(">= ",val_SensorDepth[9]," standard deviations within "
                              ,val_SensorDepth[10]," hours")
                     , paste0("> ",val_SensorDepth[12]
                              ," consecutive measurements within ",val_SensorDepth[13]
                              ," units of one another"))
# Discharge
nam_Discharge <- c("myLab.Discharge"                        #1
                   , "myUnits.Discharge"                    #2
                   , "myThresh.Gross.Fail.Hi.Discharge"     #3
                   , "myThresh.Gross.Fail.Lo.Discharge"     #4
                   , "myThresh.Gross.Suspect.Hi.Discharge"  #5
                   , "myThresh.Gross.Suspect.Lo.Discharge"  #6
                   , "myThresh.Spike.Hi.Discharge"          #7
                   , "myThresh.Spike.Lo.Discharge"          #8
                   , "myThresh.RoC.SD.number.Discharge"     #9
                   , "myThresh.RoC.SD.period.Discharge"     #10
                   , "myThresh.Flat.Hi.Discharge"           #11
                   , "myThresh.Flat.Lo.Discharge"           #12
                   , "myThresh.Flat.Tolerance.Discharge"    #13
                   )
val_Discharge <- mget(nam_Discharge, envir=ContData.env)
txt_Discharge_F <- c(val_Discharge[1]
                     , "Fail"
                     , paste0("> ",val_Discharge[3]," ",val_Discharge[2]
                              ,"  or < ",val_Discharge[4]," ",val_Discharge[2])
                     , paste0(">= ", val_Discharge[7]," ",val_Discharge[2]," (+/-)")
                     , "NA"
                     , paste0("> ",val_Discharge[11]
                              ," consecutive measurements within ",val_Discharge[13]
                              ," units of one another"))
txt_Discharge_S <- c(val_Discharge[1]
                     , "Suspect"
                     , paste0("> ",val_Discharge[5]," ",val_Discharge[2]
                              ," or < ",val_Discharge[6]," ",val_Discharge[2])
                     , paste0(">= ", val_Discharge[8]," ",val_Discharge[2]," (+/-)")
                     , paste0(">= ",val_Discharge[9]," standard deviations within "
                              ,val_Discharge[10]," hours")
                     , paste0("> ",val_Discharge[12]
                              ," consecutive measurements within ",val_Discharge[13]
                              ," units of one another"))
# WaterLevel
nam_WaterLevel <- c("myLab.WaterLevel"                          #1
                   , "myUnits.WaterLevel"                    #2
                   , "myThresh.Gross.Fail.Hi.WaterLevel"     #3
                   , "myThresh.Gross.Fail.Lo.WaterLevel"     #4
                   , "myThresh.Gross.Suspect.Hi.WaterLevel"  #5
                   , "myThresh.Gross.Suspect.Lo.WaterLevel"  #6
                   , "myThresh.Spike.Hi.WaterLevel"          #7 -removed
                   , "myThresh.Spike.Lo.WaterLevel"          #8 - removed
                   , "myThresh.RoC.SD.number.WaterLevel"     #9 - 7
                   , "myThresh.RoC.SD.period.WaterLevel"     #10 - 8
                   , "myThresh.Flat.Hi.WaterLevel"           #11 - 9
                   , "myThresh.Flat.Lo.WaterLevel"           #12 - 10
                   , "myThresh.Flat.Tolerance.WaterLevel"    #13 - 11
                   )
val_WaterLevel <- mget(nam_WaterLevel, envir=ContData.env)
txt_WaterLevel_F <- c(val_WaterLevel[1]
                     , "Fail"
                     , paste0("> ",val_WaterLevel[3]," ",val_WaterLevel[2]
                              ,"  or < ",val_WaterLevel[4]," ",val_WaterLevel[2])
                     , "NA"
                     , "NA"
                     , paste0("> ",val_WaterLevel[9]
                              ," consecutive measurements within ",val_WaterLevel[11]
                              ," units of one another"))
txt_WaterLevel_S <- c(val_WaterLevel[1]
                     , "Suspect"
                     , paste0("> ",val_WaterLevel[5]," ",val_WaterLevel[2]
                              ," or < ",val_WaterLevel[6]," ",val_WaterLevel[2])
                     , "NA"
                     , paste0(">= ",val_WaterLevel[7]," standard deviations within "
                              ,val_WaterLevel[8]," hours")
                     , paste0("> ",val_WaterLevel[10]
                              ," consecutive measurements within ",val_WaterLevel[11]
                              ," units of one another"))

# Cond
nam_Cond <- c("myLab.Cond"                             #1
                   , "myUnits.Cond"                    #2
                   , "myThresh.Gross.Fail.Hi.Cond"     #3
                   , "myThresh.Gross.Fail.Lo.Cond"     #4
                   , "myThresh.Gross.Suspect.Hi.Cond"  #5
                   , "myThresh.Gross.Suspect.Lo.Cond"  #6
                   , "myThresh.Spike.Hi.Cond"          #7
                   , "myThresh.Spike.Lo.Cond"          #8
                   , "myThresh.RoC.SD.number.Cond"     #9
                   , "myThresh.RoC.SD.period.Cond"     #10
                   , "myThresh.Flat.Hi.Cond"           #11
                   , "myThresh.Flat.Lo.Cond"           #12
                   , "myThresh.Flat.Tolerance.Cond"    #13
                   )
val_Cond <- mget(nam_Cond, envir=ContData.env)
txt_Cond_F <- c(val_Cond[1]
                     , "Fail"
                     , paste0("> ",val_Cond[3]," ",val_Cond[2]
                              ,"  or < ",val_Cond[4]," ",val_Cond[2])
                     , paste0(">= ", val_Cond[7]," ",val_Cond[2]," (+/-)")
                     , "NA"
                     , paste0("> ",val_Cond[11]
                              ," consecutive measurements within ",val_Cond[13]
                              ," units of one another"))
txt_Cond_S <- c(val_Cond[1]
                     , "Suspect"
                     , paste0("> ",val_Cond[5]," ",val_Cond[2]
                              ," or < ",val_Cond[6]," ",val_Cond[2])
                     , paste0(">= ", val_Cond[8]," ",val_Cond[2]," (+/-)")
                     , paste0(">= ",val_Cond[9]," standard deviations within "
                              ,val_Cond[10]," hours")
                     , paste0("> ",val_Cond[12]
                              ," consecutive measurements within ",val_Cond[13]
                              ," units of one another"))
# DO
nam_DO <- c("myLab.DO"                         #1
             , "myUnits.DO"                    #2
             , "myThresh.Gross.Fail.Hi.DO"     #3
             , "myThresh.Gross.Fail.Lo.DO"     #4
             , "myThresh.Gross.Suspect.Hi.DO"  #5
             , "myThresh.Gross.Suspect.Lo.DO"  #6
             , "myThresh.Spike.Hi.DO"          #7
             , "myThresh.Spike.Lo.DO"          #8
             , "myThresh.RoC.SD.number.DO"     #9
             , "myThresh.RoC.SD.period.DO"     #10
             , "myThresh.Flat.Hi.DO"           #11
             , "myThresh.Flat.Lo.DO"           #12
             , "myThresh.Flat.Tolerance.DO"    #13
             )
val_DO <- mget(nam_DO, envir=ContData.env)
txt_DO_F <- c(val_DO[1]
                     , "Fail"
                     , paste0("> ",val_DO[3]," ",val_DO[2]
                              ,"  or < ",val_DO[4]," ",val_DO[2])
                     , paste0(">= ", val_DO[7]," ",val_DO[2]," (+/-)")
                     , "NA"
                     , paste0("> ",val_DO[11]
                              ," consecutive measurements within ",val_DO[13]
                              ," units of one another"))
txt_DO_S <- c(val_DO[1]
                     , "Suspect"
                     , paste0("> ",val_DO[5]," ",val_DO[2]
                              ," or < ",val_DO[6]," ",val_DO[2])
                     , paste0(">= ", val_DO[8]," ",val_DO[2]," (+/-)")
                     , paste0(">= ",val_DO[9]," standard deviations within "
                              ,val_DO[10]," hours")
                     , paste0("> ",val_DO[12]
                              ," consecutive measurements within ",val_DO[13]
                              ," units of one another"))

# DO.adj
nam_DO.adj <- c("myLab.DO.adj"                         #1
             , "myUnits.DO.adj"                    #2
             , "myThresh.Gross.Fail.Hi.DO.adj"     #3
             , "myThresh.Gross.Fail.Lo.DO.adj"     #4
             , "myThresh.Gross.Suspect.Hi.DO.adj"  #5
             , "myThresh.Gross.Suspect.Lo.DO.adj"  #6
             , "myThresh.Spike.Hi.DO.adj"          #7
             , "myThresh.Spike.Lo.DO.adj"          #8
             , "myThresh.RoC.SD.number.DO.adj"     #9
             , "myThresh.RoC.SD.period.DO.adj"     #10
             , "myThresh.Flat.Hi.DO.adj"           #11
             , "myThresh.Flat.Lo.DO.adj"           #12
             , "myThresh.Flat.Tolerance.DO.adj"    #13
             )
val_DO.adj <- mget(nam_DO.adj, envir=ContData.env)
txt_DO.adj_F <- c(val_DO.adj[1]
                     , "Fail"
                     , paste0("> ",val_DO.adj[3]," ",val_DO.adj[2]
                              ,"  or < ",val_DO.adj[4]," ",val_DO.adj[2])
                     , paste0(">= ", val_DO.adj[7]," ",val_DO.adj[2]," (+/-)")
                     , "NA"
                     , paste0("> ",val_DO.adj[11]
                              ," consecutive measurements within ",val_DO.adj[13]
                              ," units of one another"))
txt_DO.adj_S <- c(val_DO.adj[1]
                     , "Suspect"
                     , paste0("> ",val_DO.adj[5]," ",val_DO.adj[2]
                              ," or < ",val_DO.adj[6]," ",val_DO.adj[2])
                     , paste0(">= ", val_DO.adj[8]," ",val_DO.adj[2]," (+/-)")
                     , paste0(">= ",val_DO[9]," standard deviations within "
                              ,val_DO[10]," hours")
                     , paste0("> ",val_DO[12]
                              ," consecutive measurements within ",val_DO.adj[13]
                              ," units of one another"))

# DO.pctsat
nam_DO.pctsat <- c("myLab.DO.pctsat"                         #1
             , "myUnits.DO.pctsat"                    #2
             , "myThresh.Gross.Fail.Hi.DO.pctsat"     #3
             , "myThresh.Gross.Fail.Lo.DO.pctsat"     #4
             , "myThresh.Gross.Suspect.Hi.DO.pctsat"  #5
             , "myThresh.Gross.Suspect.Lo.DO.pctsat"  #6
             , "myThresh.Spike.Hi.DO.pctsat"          #7
             , "myThresh.Spike.Lo.DO.pctsat"          #8
             , "myThresh.RoC.SD.number.DO.pctsat"     #9
             , "myThresh.RoC.SD.period.DO.pctsat"     #10
             , "myThresh.Flat.Hi.DO.pctsat"           #11
             , "myThresh.Flat.Lo.DO.pctsat"           #12
             , "myThresh.Flat.Tolerance.DO.pctsat"    #13
             )
val_DO.pctsat <- mget(nam_DO.pctsat, envir=ContData.env)
txt_DO.pctsat_F <- c(val_DO.pctsat[1]
                     , "Fail"
                     , paste0("> ",val_DO.pctsat[3]," ",val_DO.pctsat[2]
                              ,"  or < ",val_DO.pctsat[4]," ",val_DO.pctsat[2])
                     , paste0(">= ", val_DO.pctsat[7]," ",val_DO.pctsat[2]," (+/-)")
                     , "NA"
                     , paste0("> ",val_DO.pctsat[11]
                              ," consecutive measurements within ",val_DO.pctsat[13]
                              ," units of one another"))
txt_DO.pctsat_S <- c(val_DO.pctsat[1]
                     , "Suspect"
                     , paste0("> ",val_DO.pctsat[5]," ",val_DO.pctsat[2]
                              ," or < ",val_DO.pctsat[6]," ",val_DO.pctsat[2])
                     , paste0(">= ", val_DO.pctsat[8]," ",val_DO.pctsat[2]," (+/-)")
                     , paste0(">= ",val_DO.pctsat[9]," standard deviations within "
                              ,val_DO.pctsat[10]," hours")
                     , paste0("> ",val_DO.pctsat[12]
                              ," consecutive measurements within ",val_DO.pctsat[13]
                              ," units of one another"))

# pH
nam_pH <- c("myLab.pH"                       #1
           , "myUnits.pH"                    #2
           , "myThresh.Gross.Fail.Hi.pH"     #3
           , "myThresh.Gross.Fail.Lo.pH"     #4
           , "myThresh.Gross.Suspect.Hi.pH"  #5
           , "myThresh.Gross.Suspect.Lo.pH"  #6
           , "myThresh.Spike.Hi.pH"          #7
           , "myThresh.Spike.Lo.pH"          #8
           , "myThresh.RoC.SD.number.pH"     #9
           , "myThresh.RoC.SD.period.pH"     #10
           , "myThresh.Flat.Hi.pH"           #11
           , "myThresh.Flat.Lo.pH"           #12
           , "myThresh.Flat.Tolerance.pH"    #13
           )
val_pH <- mget(nam_pH, envir=ContData.env)
txt_pH_F <- c(val_pH[1]
                     , "Fail"
                     , paste0("> ",val_pH[3]," ",val_pH[2]
                              ,"  or < ",val_pH[4]," ",val_pH[2])
                     , paste0(">= ", val_pH[7]," ",val_pH[2]," (+/-)")
                     , "NA"
                     , paste0("> ",val_pH[11]
                              ," consecutive measurements within ",val_pH[13]
                              ," units of one another"))
txt_pH_S <- c(val_pH[1]
                     , "Suspect"
                     , paste0("> ",val_pH[5]," ",val_pH[2]
                              ," or < ",val_pH[6]," ",val_pH[2])
                     , paste0(">= ", val_pH[8]," ",val_pH[2]," (+/-)")
                     , paste0(">= ",val_pH[9]," standard deviations within "
                              ,val_pH[10]," hours")
                     , paste0("> ",val_pH[12]
                              ," consecutive measurements within ",val_pH[13]
                              ," units of one another"))
# Turbidity
nam_Turbidity <- c("myLab.Turbidity"                        #1
                   , "myUnits.Turbidity"                    #2
                   , "myThresh.Gross.Fail.Hi.Turbidity"     #3
                   , "myThresh.Gross.Fail.Lo.Turbidity"     #4
                   , "myThresh.Gross.Suspect.Hi.Turbidity"  #5
                   , "myThresh.Gross.Suspect.Lo.Turbidity"  #6
                   , "myThresh.Spike.Hi.Turbidity"          #7
                   , "myThresh.Spike.Lo.Turbidity"          #8
                   , "myThresh.RoC.SD.number.Turbidity"     #9
                   , "myThresh.RoC.SD.period.Turbidity"     #10
                   , "myThresh.Flat.Hi.Turbidity"           #11
                   , "myThresh.Flat.Lo.Turbidity"           #12
                   , "myThresh.Flat.Tolerance.Turbidity"    #13
                   )
val_Turbidity <- mget(nam_Turbidity, envir=ContData.env)
txt_Turbidity_F <- c(val_Turbidity[1]
                     , "Fail"
                     , paste0("> ",val_Turbidity[3]," ",val_Turbidity[2]
                              ,"  or < ",val_Turbidity[4]," ",val_Turbidity[2])
                     , paste0(">= ", val_Turbidity[7]," ",val_Turbidity[2]," (+/-)")
                     , "NA"
                     , paste0("> ",val_Turbidity[11]
                              ," consecutive measurements within ",val_Turbidity[13]
                              ," units of one another"))
txt_Turbidity_S <- c(val_Turbidity[1]
                     , "Suspect"
                     , paste0("> ",val_Turbidity[5]," ",val_Turbidity[2]
                              ," or < ",val_Turbidity[6]," ",val_Turbidity[2])
                     , paste0(">= ", val_Turbidity[8]," ",val_Turbidity[2]," (+/-)")
                     , paste0(">= ",val_Turbidity[9]," standard deviations within "
                              ,val_Turbidity[10]," hours")
                     , paste0("> ",val_Turbidity[12]
                              ," consecutive measurements within ",val_Turbidity[13]
                              ," units of one another"))
# Chlorophylla
nam_Chlorophylla <- c("myLab.Chlorophylla"                     #1
                   , "myUnits.Chlorophylla"                    #2
                   , "myThresh.Gross.Fail.Hi.Chlorophylla"     #3
                   , "myThresh.Gross.Fail.Lo.Chlorophylla"     #4
                   , "myThresh.Gross.Suspect.Hi.Chlorophylla"  #5
                   , "myThresh.Gross.Suspect.Lo.Chlorophylla"  #6
                   , "myThresh.Spike.Hi.Chlorophylla"          #7
                   , "myThresh.Spike.Lo.Chlorophylla"          #8
                   , "myThresh.RoC.SD.number.Chlorophylla"     #9
                   , "myThresh.RoC.SD.period.Chlorophylla"     #10
                   , "myThresh.Flat.Hi.Chlorophylla"           #11
                   , "myThresh.Flat.Lo.Chlorophylla"           #12
                   , "myThresh.Flat.Tolerance.Chlorophylla"    #13
                   )
val_Chlorophylla <- mget(nam_Chlorophylla, envir=ContData.env)
txt_Chlorophylla_F <- c(val_Chlorophylla[1]
                     , "Fail"
                     , paste0("> ",val_Chlorophylla[3]," ",val_Chlorophylla[2]
                              ,"  or < ",val_Chlorophylla[4]," ",val_Chlorophylla[2])
                     , paste0(">= ", val_Chlorophylla[7]," ",val_Chlorophylla[2]," (+/-)")
                     , "NA"
                     , paste0("> ",val_Chlorophylla[11]
                              ," consecutive measurements within ",val_Chlorophylla[13]
                              ," units of one another"))
txt_Chlorophylla_S <- c(val_Chlorophylla[1]
                     , "Suspect"
                     , paste0("> ",val_Chlorophylla[5]," ",val_Chlorophylla[2]
                              ," or < ",val_Chlorophylla[6]," ",val_Chlorophylla[2])
                     , paste0(">= ", val_Chlorophylla[8]," ",val_Chlorophylla[2]," (+/-)")
                     , paste0(">= ",val_Chlorophylla[9]," standard deviations within "
                              ,val_Chlorophylla[10]," hours")
                     , paste0("> ",val_Chlorophylla[12]
                              ," consecutive measurements within ",val_Chlorophylla[13]
                              ," units of one another"))

              
## Salinity
nam_Salinity <- c("myLab.Salinity"                       #1
           , "myUnits.Salinity"                    #2
           , "myThresh.Gross.Fail.Hi.Salinity"     #3
           , "myThresh.Gross.Fail.Lo.Salinity"     #4
           , "myThresh.Gross.Suspect.Hi.Salinity"  #5
           , "myThresh.Gross.Suspect.Lo.Salinity"  #6
           , "myThresh.Spike.Hi.Salinity"          #7
           , "myThresh.Spike.Lo.Salinity"          #8
           , "myThresh.RoC.SD.number.Salinity"     #9
           , "myThresh.RoC.SD.period.Salinity"     #10
           , "myThresh.Flat.Hi.Salinity"           #11
           , "myThresh.Flat.Lo.Salinity"           #12
           , "myThresh.Flat.Tolerance.Salinity"    #13
           )
val_Salinity <- mget(nam_Salinity, envir=ContData.env)
txt_Salinity_F <- c(val_Salinity[1]
                     , "Fail"
                     , paste0("> ",val_Salinity[3]," ",val_Salinity[2]
                              ,"  or < ",val_Salinity[4]," ",val_Salinity[2])
                     , paste0(">= ", val_Salinity[7]," ",val_Salinity[2]," (+/-)")
                     , "NA"
                     , paste0("> ",val_Salinity[11]
                              ," consecutive measurements within ",val_Salinity[13]
                              ," units of one another"))
txt_Salinity_S <- c(val_Salinity[1]
                     , "Suspect"
                     , paste0("> ",val_Salinity[5]," ",val_Salinity[2]
                              ," or < ",val_Salinity[6]," ",val_Salinity[2])
                     , paste0(">= ", val_Salinity[8]," ",val_Salinity[2]," (+/-)")
                     , paste0(">= ",val_Salinity[9]," standard deviations within "
                              ,val_Salinity[10]," hours")
                     , paste0("> ",val_Salinity[12]
                              ," consecutive measurements within ",val_Salinity[13]
                              ," units of one another"))

# Create Table
df_Env <- data.frame(rbind(txt_WaterTemp_F, txt_WaterTemp_S
                           , txt_AirTemp_F, txt_AirTemp_S
                           , txt_WaterP_F, txt_WaterP_S
                           , txt_AirBP_F, txt_AirBP_S
                           , txt_SensorDepth_F, txt_SensorDepth_S
                           , txt_WaterLevel_F, txt_WaterLevel_S
                           , txt_Discharge_F, txt_Discharge_S
                           , txt_Cond_F, txt_Cond_S
                           , txt_DO_F, txt_DO_S
                           , txt_DO.adj_F, txt_DO.adj_S
                           , txt_DO.pctsat_F, txt_DO.pctsat_S
                           , txt_pH_F, txt_pH_S
                           , txt_Turbidity_F, txt_Turbidity_S
                           , txt_Chlorophylla_F, txt_Chlorophylla_S
                           , txt_Salinity_F, txt_Salinity_S
                           )
                     , row.names = NULL)
names(df_Env) <- txt_header
knitr::kable(df_Env, caption = kbl_caption)

```

## All Settings, Alphabetical
All settings listed by name in alphabetical order with values.
```{r Kable_ALL}
# sapply(ls(ContData.env), function(x) get(x, envir=ContData.env))

kbl_caption <- "Thresholds, ALL, Alphabetical"
env_Nam <- ls(ContData.env)
env_Val <- mget(env_Nam, envir=ContData.env)
df_Env <- data.frame(cbind(env_Nam, env_Val), row.names = NULL)
names(df_Env) <- c("Names", "Values")
knitr::kable(df_Env, caption = kbl_caption)

```

## All Settings, Categories
All settings by category listed by name with values.

The order presented here is the order in the config file.

### Column Names
* Acceptable column names for the data
* Units
* Logger Fields
* Parameters as appear in logger files
* Plot Labels
```{r Kable_ColumnNames}
kbl_caption <- "Thresholds, Column Names"
env_Nam <- c("myDelim"
             , "myName.SiteID"
             , "myName.Date"
             , "myName.Time"
             , "myName.DateTime"
             , "myUnits.AirTemp"
             , "myUnits.WaterTemp"
             , "myUnits.AirBP"
             , "myUnits.WaterP"
             , "myUnits.SensorDepth"
             , "myUnits.WaterLevel"
             , "myUnits.Discharge"
             , "myUnits.Cond"
             , "myUnits.DO"
             , "myUnits.DO.adj"
             , "myUnits.DO.pctsat"
             , "myUnits.pH"
             , "myUnits.Turbidity"
             , "myUnits.Chlorophylla"
             , "myUnits.Salinity"
             , "myName.RowID.Water"
             , "myName.LoggerID.Water"
             , "myName.RowID.Air"
             , "myName.LoggerID.Air"
             , "myName.WaterTemp"
             , "myName.AirTemp"
             , "myName.WaterP"
             , "myName.AirBP"
             , "myName.SensorDepth"
             , "myName.WaterLevel"
             , "myName.Discharge"
             , "myName.Cond"
             , "myName.DO"
             , "myName.DO.adj"
             , "myName.DO.pctsat"
             , "myName.pH"
             , "myName.Turbidity"
             , "myName.Chlorophylla"
             , "myName.Salinity"
             , "myLab.WaterTemp"
             , "myLab.AirTemp"
             , "myLab.Date"
             , "myLab.DateTime"
             , "myLab.WaterP"
             , "myLab.AirBP"
             , "myLab.SensorDepth"
             , "myLab.WaterLevel"
             , "myLab.Temp.BOTH"
             , "myLab.Discharge"
             , "myLab.Cond"
             , "myLab.DO"
             , "myLab.DO.adj"
             , "myLab.DO.pctsat"
             , "myLab.pH"
             , "myLab.Turbidity"
             , "myLab.Chlorophylla"
             , "myLab.Salinity"
             )
env_Val <- mget(env_Nam, envir=ContData.env)
df_Env <- data.frame(cbind(env_Nam, env_Val), row.names = NULL)
names(df_Env) <- c("Names", "Values")
knitr::kable(df_Env, caption = kbl_caption)
```

### Discrete Measurements
* Discrete, Names
* Discrete, Labels
```{r Kable_DiscreteMeasurements}
kbl_caption <- "Thresholds, Discrete Measurements"
env_Nam <- c("myPrefix.Discrete"
             , "myName.Discrete.WaterTemp"
             , "myName.Discrete.AirTemp"
             , "myName.Discrete.WaterP"
             , "myName.Discrete.AirBP"
             , "myName.Discrete.SensorDepth"
             , "myName.Discrete.WaterLevel"
             , "myName.Discrete.Discharge"
             , "myName.Discrete.Cond"
             , "myName.Discrete.DO"
             , "myName.Discrete.DO.adj"
             , "myName.Discrete.DO.pctsat"
             , "myName.Discrete.pH"
             , "myName.Discrete.Turbidity"
             , "myName.Discrete.Chlorophylla"
             , "myName.Discrete.Salinity"
             , "myLab.Discrete.WaterTemp"
             , "myLab.Discrete.AirTemp"
             , "myLab.Discrete.WaterP"
             , "myLab.Discrete.AirBP"
             , "myLab.Discrete.SensorDepth"
             , "myLab.Discrete.Discharge"
             , "myLab.Discrete.WaterLevel"
             , "myLab.Discrete.Cond"
             , "myLab.Discrete.DO"
             , "myLab.Discrete.DO.adj"
             , "myLab.Discrete.DO.pctsat"
             , "myLab.Discrete.pH"
             , "myLab.Discrete.Turbidity"
             , "myLab.Discrete.Chlorophylla"
             , "myLab.Discrete.Salinity"
             )
env_Val <- mget(env_Nam, envir=ContData.env)
df_Env <- data.frame(cbind(env_Nam, env_Val), row.names = NULL)
names(df_Env) <- c("Names", "Values")
knitr::kable(df_Env, caption = kbl_caption)
```

### Automated QC Stuff
* data type/stages
```{r Kable_AutomatedQCStuff}
kbl_caption <- "Thresholds, Automated QC Stuff"
env_Nam <- c("myDataQuality.Raw"
             , "myDataQuality.QCauto"
             , "myDataQuality.QCmanual"
             , "myDataQuality.Final"
             , "myDataQuality.Aggregated"
             )
env_Val <- mget(env_Nam, envir=ContData.env)
df_Env <- data.frame(cbind(env_Nam, env_Val), row.names = NULL)
names(df_Env) <- c("Names", "Values")
knitr::kable(df_Env, caption = kbl_caption)
```

### Directory Names
```{r Kable_DirectoryNames}
kbl_caption <- "Thresholds, Directory Names"
env_Nam <- c("myName.Dir.1Raw"
             , "myName.Dir.2QC"
             , "myName.Dir.3Agg"
             , "myName.Dir.4Stats"
             )
env_Val <- mget(env_Nam, envir=ContData.env)
df_Env <- data.frame(cbind(env_Nam, env_Val), row.names = NULL)
names(df_Env) <- c("Names", "Values")
knitr::kable(df_Env, caption = kbl_caption)
```

### Data Fields
* Field Names
* Field Labels for plots
```{r Kable_DataFields}
kbl_caption <- "Thresholds, Data Fields"
env_Nam <- c("myNames.DataFields"
             , "myNames.DataFields.Lab"
             , "myNames.DataFields.Col"
             )
env_Val <- mget(env_Nam, envir=ContData.env)
df_Env <- data.frame(cbind(env_Nam, env_Val), row.names = NULL)
names(df_Env) <- c("Names", "Values")
knitr::kable(df_Env, caption = kbl_caption)
```

### Data Quality Flag Values
```{r Kable_DataQualityFlagValues}
kbl_caption <- "Thresholds, Data Quality Flag Values"
env_Nam <- c("myFlagVal.Pass"
             , "myFlagVal.NotEval"
             , "myFlagVal.Suspect"
             , "myFlagVal.Fail"
             , "myFlagVal.NoData"
             , "myFlagVal.Order"
             )
env_Val <- mget(env_Nam, envir=ContData.env)
df_Env <- data.frame(cbind(env_Nam, env_Val), row.names = NULL)
names(df_Env) <- c("Names", "Values")
knitr::kable(df_Env, caption = kbl_caption)
```

### QC Tests and Calculations
Parameters grouped by type of QC check.

#### Gross Min/Max, Fail (equipment)
Examines values as outliers versus threholds.

* if value >= Hi or <= Lo then flagged as "Fail"
```{r Kable_QCFlags_Gross_Fail}
kbl_caption <- "Thresholds, QC Tests and Calculations, Gross Min/Max, Fail (equipment)"
env_Nam <- c("myThresh.Gross.Fail.Hi.WaterTemp"
             , "myThresh.Gross.Fail.Lo.WaterTemp"
             , "myThresh.Gross.Fail.Hi.AirTemp"
             , "myThresh.Gross.Fail.Lo.AirTemp"
             , "myThresh.Gross.Fail.Hi.WaterP"
             , "myThresh.Gross.Fail.Lo.WaterP"
             , "myThresh.Gross.Fail.Hi.AirBP"
             , "myThresh.Gross.Fail.Lo.AirBP"
             , "myThresh.Gross.Fail.Hi.SensorDepth"
             , "myThresh.Gross.Fail.Lo.SensorDepth"
             , "myThresh.Gross.Fail.Hi.WaterLevel"
             , "myThresh.Gross.Fail.Lo.WaterLevel"
             , "myThresh.Gross.Fail.Hi.Discharge"
             , "myThresh.Gross.Fail.Lo.Discharge"
             , "myThresh.Gross.Fail.Hi.Cond"
             , "myThresh.Gross.Fail.Lo.Cond"
             , "myThresh.Gross.Fail.Hi.DO"
             , "myThresh.Gross.Fail.Lo.DO"
             , "myThresh.Gross.Fail.Hi.DO.adj"
             , "myThresh.Gross.Fail.Lo.DO.adj"
             , "myThresh.Gross.Fail.Hi.DO.pctsat"
             , "myThresh.Gross.Fail.Lo.DO.pctsat"
             , "myThresh.Gross.Fail.Hi.pH"
             , "myThresh.Gross.Fail.Lo.pH"
             , "myThresh.Gross.Fail.Hi.Turbidity"
             , "myThresh.Gross.Fail.Lo.Turbidity"
             , "myThresh.Gross.Fail.Hi.Chlorophylla"
             , "myThresh.Gross.Fail.Lo.Chlorophylla"
             , "myThresh.Gross.Fail.Hi.Salinity"
             , "myThresh.Gross.Fail.Lo.Salinity"
             )
env_Val <- mget(env_Nam, envir=ContData.env)
df_Env <- data.frame(cbind(env_Nam, env_Val), row.names = NULL)
names(df_Env) <- c("Names", "Values")
knitr::kable(df_Env, caption = kbl_caption)
```

#### Gross Min/Max, Suspect (extreme)
Examines values as outliers versus threholds.

* if value >= Hi or <= Lo then flagged as "Suspect"
```{r Kable_QCFlags_Gross_Suspect}
kbl_caption <- "Thresholds, QC Tests and Calculations, Gross Min/Max, Fail (equipment)"
env_Nam <- c("myThresh.Gross.Suspect.Hi.WaterTemp"
             , "myThresh.Gross.Suspect.Lo.WaterTemp"
             , "myThresh.Gross.Suspect.Hi.AirTemp"
             , "myThresh.Gross.Suspect.Lo.AirTemp"
             , "myThresh.Gross.Suspect.Hi.WaterP"
             , "myThresh.Gross.Suspect.Lo.WaterP"
             , "myThresh.Gross.Suspect.Hi.AirBP"
             , "myThresh.Gross.Suspect.Lo.AirBP"
             , "myThresh.Gross.Suspect.Hi.SensorDepth"
             , "myThresh.Gross.Suspect.Lo.SensorDepth"
             , "myThresh.Gross.Suspect.Hi.WaterLevel"
             , "myThresh.Gross.Suspect.Lo.WaterLevel"
             , "myThresh.Gross.Suspect.Hi.Discharge"
             , "myThresh.Gross.Suspect.Lo.Discharge"
             , "myThresh.Gross.Suspect.Hi.Cond"
             , "myThresh.Gross.Suspect.Lo.Cond"
             , "myThresh.Gross.Suspect.Hi.DO"
             , "myThresh.Gross.Suspect.Lo.DO"
             , "myThresh.Gross.Suspect.Hi.DO.adj"
             , "myThresh.Gross.Suspect.Lo.DO.adj"
             , "myThresh.Gross.Suspect.Hi.DO.pctsat"
             , "myThresh.Gross.Suspect.Lo.DO.pctsat"
             , "myThresh.Gross.Suspect.Hi.pH"
             , "myThresh.Gross.Suspect.Lo.pH"
             , "myThresh.Gross.Suspect.Hi.Turbidity"
             , "myThresh.Gross.Suspect.Lo.Turbidity"
             , "myThresh.Gross.Suspect.Hi.Chlorophylla"
             , "myThresh.Gross.Suspect.Lo.Chlorophylla"
             , "myThresh.Gross.Suspect.Hi.Salinity"
             , "myThresh.Gross.Suspect.Lo.Salinity"
             )
env_Val <- mget(env_Nam, envir=ContData.env)
df_Env <- data.frame(cbind(env_Nam, env_Val), row.names = NULL)
names(df_Env) <- c("Names", "Values")
knitr::kable(df_Env, caption = kbl_caption)
```

#### Spike thresholds (absolute change)
Examines difference between consecutive measurements.

* if delta >= Hi then flagged as "Fail"
* if delta >= Lo then flagged as "Suspect"
```{r Kable_QCFlags_Spike}
kbl_caption <- "Thresholds, QC Tests and Calculations, Spike thresholds (absolute change)"
env_Nam <- c("myThresh.Spike.Hi.WaterTemp"
             , "myThresh.Spike.Lo.WaterTemp"
             , "myThresh.Spike.Hi.AirTemp"
             , "myThresh.Spike.Lo.AirTemp"
             , "myThresh.Spike.Hi.WaterP"
             , "myThresh.Spike.Lo.WaterP"
             , "myThresh.Spike.Hi.AirBP"
             , "myThresh.Spike.Lo.AirBP"
             , "myThresh.Spike.Hi.SensorDepth"
             , "myThresh.Spike.Lo.SensorDepth"
             , "myThresh.Spike.Hi.WaterLevel"
             , "myThresh.Spike.Lo.WaterLevel"
             , "myThresh.Spike.Hi.Discharge"
             , "myThresh.Spike.Lo.Discharge"
             , "myThresh.Spike.Hi.Cond"
             , "myThresh.Spike.Lo.Cond"
             , "myThresh.Spike.Hi.DO"
             , "myThresh.Spike.Lo.DO"
             , "myThresh.Spike.Hi.DO.adj"
             , "myThresh.Spike.Lo.DO.adj"
             , "myThresh.Spike.Hi.DO.pctsat"
             , "myThresh.Spike.Lo.DO.pctsat"
             , "myThresh.Spike.Hi.pH"
             , "myThresh.Spike.Lo.pH"
             , "myThresh.Spike.Hi.Turbidity"
             , "myThresh.Spike.Lo.Turbidity"
             , "myThresh.Spike.Hi.Chlorophylla"
             , "myThresh.Spike.Lo.Chlorophylla"
             , "myThresh.Spike.Hi.Salinity"
             , "myThresh.Spike.Lo.Salinity"
             )
env_Val <- mget(env_Nam, envir=ContData.env)
df_Env <- data.frame(cbind(env_Nam, env_Val), row.names = NULL)
names(df_Env) <- c("Names", "Values")
knitr::kable(df_Env, caption = kbl_caption)
```

#### Rate of Change (relative change)
Examines Standard Deviation (SD) over "period" and difference in consecutive values.

* If delta >= SD.number * SD then flagged as "Suspect"
```{r Kable_QCFlags_RoC}
kbl_caption <- "Thresholds, QC Tests and Calculations, Rate of Change (relative change)"
env_Nam <- c("myDefault.RoC.SD.number"
             , "myDefault.RoC.SD.period"
             , "myThresh.RoC.SD.number.WaterTemp"
             , "myThresh.RoC.SD.period.WaterTemp"
             , "myThresh.RoC.SD.number.AirTemp"
             , "myThresh.RoC.SD.period.AirTemp"
             , "myThresh.RoC.SD.number.WaterP"
             , "myThresh.RoC.SD.period.WaterP"
             , "myThresh.RoC.SD.number.AirBP"
             , "myThresh.RoC.SD.period.AirBP"
             , "myThresh.RoC.SD.number.SensorDepth"
             , "myThresh.RoC.SD.period.SensorDepth"
             , "myThresh.RoC.SD.number.WaterLevel"
             , "myThresh.RoC.SD.period.WaterLevel"
             , "myThresh.RoC.SD.number.Discharge"
             , "myThresh.RoC.SD.period.Discharge"
             , "myThresh.RoC.SD.number.Cond"
             , "myThresh.RoC.SD.period.Cond"
             , "myThresh.RoC.SD.number.DO"
             , "myThresh.RoC.SD.period.DO"
             , "myThresh.RoC.SD.number.DO.adj"
             , "myThresh.RoC.SD.period.DO.adj"
             , "myThresh.RoC.SD.number.DO.pctsat"
             , "myThresh.RoC.SD.period.DO.pctsat"
             , "myThresh.RoC.SD.number.pH"
             , "myThresh.RoC.SD.period.pH"
             , "myThresh.RoC.SD.number.Turbidity"
             , "myThresh.RoC.SD.period.Turbidity"
             , "myThresh.RoC.SD.number.Chlorophylla"
             , "myThresh.RoC.SD.period.Chlorophylla"
             , "myThresh.RoC.SD.number.Salinity"
             , "myThresh.RoC.SD.period.Salinity"
             )
env_Val <- mget(env_Nam, envir=ContData.env)
df_Env <- data.frame(cbind(env_Nam, env_Val), row.names = NULL)
names(df_Env) <- c("Names", "Values")
knitr::kable(df_Env, caption = kbl_caption)
```

#### No Change (flat-line)
Examines consecutive values within "Tolerance" of each other.

* If number of consecutive values >= Hi then flagged as "Fail"
* If number of consecutive values >= Lo (and < Hi) then flagged as "Suspect"
```{r Kable_QCFlags_Flat}
kbl_caption <- "Thresholds, QC Tests and Calculations, No Change (flat-line)"
env_Nam <- c("myDefault.Flat.Hi"
             , "myDefault.Flat.Lo"
             , "myDefault.Flat.Tolerance"
             , "myThresh.Flat.Hi.WaterTemp"
             , "myThresh.Flat.Lo.WaterTemp"
             , "myThresh.Flat.Tolerance.WaterTemp"
             , "myThresh.Flat.Hi.AirTemp"
             , "myThresh.Flat.Lo.AirTemp"
             , "myThresh.Flat.Tolerance.AirTemp"
             , "myThresh.Flat.Hi.WaterP"
             , "myThresh.Flat.Lo.WaterP"
             , "myThresh.Flat.Tolerance.WaterP"
             , "myThresh.Flat.Hi.AirBP"
             , "myThresh.Flat.Lo.AirBP"
             , "myThresh.Flat.Tolerance.AirBP"
             , "myThresh.Flat.Hi.SensorDepth"
             , "myThresh.Flat.Lo.SensorDepth"
             , "myThresh.Flat.Tolerance.SensorDepth"
             , "myThresh.Flat.Hi.WaterLevel"
             , "myThresh.Flat.Lo.WaterLevel"
             , "myThresh.Flat.Tolerance.WaterLevel"
             , "myThresh.Flat.Hi.Discharge"
             , "myThresh.Flat.Lo.Discharge"
             , "myThresh.Flat.Tolerance.Discharge"
             , "myThresh.Flat.Hi.Cond"
             , "myThresh.Flat.Lo.Cond"
             , "myThresh.Flat.Tolerance.Cond"
             , "myThresh.Flat.Hi.DO"
             , "myThresh.Flat.Lo.DO"
             , "myThresh.Flat.Tolerance.DO"
             , "myThresh.Flat.Hi.DO.adj"
             , "myThresh.Flat.Lo.DO.adj"
             , "myThresh.Flat.Tolerance.DO.adj"
             , "myThresh.Flat.Hi.DO.pctsat"
             , "myThresh.Flat.Lo.DO.pctsat"
             , "myThresh.Flat.Tolerance.DO.pctsat"
             , "myThresh.Flat.Hi.pH"
             , "myThresh.Flat.Lo.pH"
             , "myThresh.Flat.Tolerance.pH"
             , "myThresh.Flat.Hi.Turbidity"
             , "myThresh.Flat.Lo.Turbidity"
             , "myThresh.Flat.Tolerance.Turbidity"
             , "myThresh.Flat.Hi.Chlorophylla"
             , "myThresh.Flat.Lo.Chlorophylla"
             , "myThresh.Flat.Tolerance.Chlorophylla"
             , "myThresh.Flat.Hi.Salinity"
             , "myThresh.Flat.Lo.Salinity"
             , "myThresh.Flat.Tolerance.Salinity"
             , "myThresh.Flat.MaxComp"
             )
env_Val <- mget(env_Nam, envir=ContData.env)
df_Env <- data.frame(cbind(env_Nam, env_Val), row.names = NULL)
names(df_Env) <- c("Names", "Values")
knitr::kable(df_Env, caption = kbl_caption)
```

### Data Fields with Flags
* flag labels
* Data Quality Test Names
```{r Kable_DataFieldswithFlags}
kbl_caption <- "Thresholds, Data Fields with Flags"
env_Nam <- c("myName.Flag"
             , "myNames.Cols4Flags"
             , "myNames.Flags"
             , "myName.Flag.DateTime"
             , "myName.Flag.WaterTemp"
             , "myName.Flag.AirTemp"
             , "myName.Flag.WaterP"
             , "myName.Flag.AirBP"
             , "myName.Flag.SensorDepth"
             , "myName.Flag.WaterLevel"
             , "myName.Flag.Discharge"
             , "myName.Flag.Cond"
             , "myName.Flag.DO"
             , "myName.Flag.DO.adj"
             , "myName.Flag.DO.pctsat"
             , "myName.Flag.pH"
             , "myName.Flag.Turbidity"
             , "myName.Flag.Chlorophylla"
             , "myName.Flag.Salinity"
             , "myNames.QCTests"
             , "myNames.QCCalcs"
             )
env_Val <- mget(env_Nam, envir=ContData.env)
df_Env <- data.frame(cbind(env_Nam, env_Val), row.names = NULL)
names(df_Env) <- c("Names", "Values")
knitr::kable(df_Env, caption = kbl_caption)
```

### Exceedance Values for Statistics
Exceedance values for stats (default to Gross-Suspect-Hi value) 
```{r Kable_ExceedanceValuesforStatistics}
kbl_caption <- "Thresholds, Exceedance Values for Statistics"
env_Nam <- c("myExceed.WaterTemp"
             , "myExceed.AirTemp"
             , "myExceed.SensorDepth"
             )
env_Val <- mget(env_Nam, envir=ContData.env)
df_Env <- data.frame(cbind(env_Nam, env_Val), row.names = NULL)
names(df_Env) <- c("Names", "Values")
knitr::kable(df_Env, caption = kbl_caption)
```

### Date and Time Formats
* Date and Time Formats
* Time zone
```{r Kable_DateTimeFormats}
kbl_caption <- "Thresholds, Date and Time Formats"
env_Nam <- c("myFormat.Date"
             , "myFormat.Time"
             , "myFormat.DateTime"
             , "DateRange.Start.Default"
             , "DateRange.End.Default"
             , "myTZ"
             )
env_Val <- mget(env_Nam, envir=ContData.env)
df_Env <- data.frame(cbind(env_Nam, env_Val), row.names = NULL)
names(df_Env) <- c("Names", "Values")
knitr::kable(df_Env, caption = kbl_caption)
```

### Time Frames
* Time Frames (MM-DD)
* Time Frame Names
* for summary stats
```{r Kable_TimeFrames}
kbl_caption <- "Thresholds, Time Frames"
env_Nam <- c("myTimeFrame.Annual.Start"
             , "myTimeFrame.Annual.End"
             , "myTimeFrame.WaterYear.Start"
             , "myTimeFrame.Season.Spring.Start"
             , "myTimeFrame.Season.Summer.Start"
             , "myTimeFrame.Season.Fall.Start"
             , "myTimeFrame.Season.Winter.Start"
             , "myName.Yr"
             , "myName.YrMo" 
             , "myName.Mo"  
             , "myName.MoDa"
             , "myName.JuDa" 
             , "myName.Day" 
             , "myName.Season" 
             , "myName.YrSeason" 
             , "myNames.Fields.TimePeriods"
             )
env_Val <- mget(env_Nam, envir=ContData.env)
df_Env <- data.frame(cbind(env_Nam, env_Val), row.names = NULL)
names(df_Env) <- c("Names", "Values")
knitr::kable(df_Env, caption = kbl_caption)
```

### Exclude Trigger
Trigger for Stats to exclude (TRUE) or include (FALSE) where flag = "fail"
```{r Kable_ExcludeTrigger}
kbl_caption <- "Thresholds, Exclude Trigger"
env_Nam <- c("myStats.Fails.Exclude"
             )
env_Val <- mget(env_Nam, envir=ContData.env)
df_Env <- data.frame(cbind(env_Nam, env_Val), row.names = NULL)
names(df_Env) <- c("Names", "Values")
knitr::kable(df_Env, caption = kbl_caption)
```

### Report Format
Default report format output.
```{r Kable_ReportFormat}
kbl_caption <- "Thresholds, Report Format"
env_Nam <- c("myReport.Format"
             #, "myReport.Dir"
             )
env_Val <- mget(env_Nam, envir=ContData.env)
df_Env <- data.frame(cbind(env_Nam, env_Val), row.names = NULL)
names(df_Env) <- c("Names", "Values")
knitr::kable(df_Env, caption = kbl_caption)
```
