---
title: "Data Quality Control Report"
output: html_document
---

```{r report_date, results='asis', echo=FALSE, warning=FALSE}
  myReportDate <- format(Sys.Date(),ContData.env$myFormat.Date)
  cat(paste("**Report Date:** ",myReportDate,"\n\n",sep=""))
  myUser <- Sys.getenv("USERNAME")
  cat(paste("**Generated By:** ",myUser,"\n\n",sep=""))
```

# DATA FILE INFORMATION
```{r data_file_info, results='asis', echo=FALSE, warning=FALSE}
  
  #filename
  cat("**Filename:** ",strFile,"\n\n",sep="")

  mySiteID <- data.import[1,ContData.env$myName.SiteID]
  
  cat(paste("**SiteID:** ",mySiteID,"\n\n",sep=""))
  
  if(exists("fun.myData.DateRange.Start")==TRUE){
    POR.Requested <- paste(fun.myData.DateRange.Start," to ",fun.myData.DateRange.End, sep="")
  } else {
    POR.Requested <- "NA"
  }
  cat(paste("**Period of Record, Requested:** ",POR.Requested,sep="",collapse="\n\n"))
  
  myNumRecords <- nrow(data.import) # 20170228, mod from records 10 and 11 to half way point
  
  # myTimeDiff <- difftime(data.import[10,ContData.env$myName.DateTime],data.import[11,ContData.env$myName.DateTime],units="mins")
  #x <- data.import[,ContData.env$myName.DateTime]
  myT <- strptime(data.import[,ContData.env$myName.DateTime],format=ContData.env$myFormat.DateTime)
  myTimeDiff.all <- difftime(myT[-1],myT[-length(myT)],units="mins")
  myTimeDiff <- median(as.vector(myTimeDiff.all),na.rm=TRUE)

  cat(paste("\n\n**Period of Record, Actual:** ",min(data.import[,ContData.env$myName.Date])," to ",max(data.import[,ContData.env$myName.Date]),"\n\n",sep=""))
       
  cat(paste("**Recording Interval:** ",myTimeDiff[1]," minutes\n\n",sep=""))
  
  if(exists("strFile.DataType")==TRUE){
    myDataType <- strFile.DataType
  } else {
    myDataType <- "NA"
  }
  cat(paste("**Data Type:** ",myDataType,"\n\n",sep=""))  # need to do better
  
   myParameters.ALL     <- ContData.env$myNames.DataFields[ContData.env$myNames.DataFields 
                                                           %in% names(data.import)==TRUE] 
   myParameters.Lab.ALL <- ContData.env$myNames.DataFields.Lab[ContData.env$myNames.DataFields 
                                                               %in% names(data.import)==TRUE]
   # Filter out Discrete
   myParameters     <- myParameters.ALL[!grepl(ContData.env$myPrefix.Discrete,myParameters.ALL)]
   myParameters.Lab <- myParameters.Lab.ALL[!grepl(ContData.env$myPrefix.Discrete,myParameters.Lab.ALL)]
   
   
 #cat("**Parameters:** ",paste(myParameters.Lab,", ",sep=""),"\n\n",sep="")
  # above line not working, preventing pandoc conversion to WORD
  #cat("**Included Parameters:** \n\n")
  cat("**Parameters Included:** ",paste(myParameters.ALL,", ",sep=""),"\n\n",sep="")

```

# DATA SUMMARY, OVERALL

```{r data_summary_overall, results='asis',echo=FALSE, warning=FALSE}
#     2.1. Records by Month/Day
#     split so easier to put on paper
#     number of records by month/day (split 1:15 and 16:31)
#     
  # format = markdown/pandoc = seems to be the same.  All rows but no columns in Word.
  # Have to use on table not ftable.  ftable better by itself but doesn't work with knitr::kable.

    # # QC, if days less than count = 15
    #*Error in table.  Only printing half.* (fixed for sites with <15 days)
    # if((max(data.import[,"day"])-min(data.import[,"day"]))<15) {##IF.daycount.START
    #   myTable <- table(data.import[,"month"],data.import[,"day"])
    #   print(knitr::kable(myTable, format="markdown",row.names=TRUE))
    # } else {
    #   #
    #   #myTable.month.day.rec.LTE15 <-
    #   myTable <- table(data.import[,"month"][data.import[,"day"]<=15],data.import[,"day"][data.import[,"day"]<=15])
    #     print(knitr::kable(myTable, format="markdown", row.names=TRUE))
    #     #knitr::kable(myTable.month.day.rec.LTE15, format="pandoc", caption = "Title of the table")
    #   cat("\n\n")  
    #   #   
    #   # myTable.month.day.rec.GT15 <-
    #   myTable <- table(data.import[,"month"][data.import[,"day"]>15],data.import[,"day"][data.import[,"day"]>15])
    #     print(knitr::kable(myTable, format="markdown", row.names=TRUE))
      #   
   # }##IF.daycount.END


      # Convert time interval (minutes) to number per day
      records.expected <- round(24*60/as.numeric(myTimeDiff[1]),1)
      
      cat(paste("Estimated number of records per day is ",records.expected,".",sep=""))
        cat("\n\n")

        
    cat("Number of records by year and month (with totals).")
    cat("\n")
    myTable <- addmargins(table(data.import[,ContData.env$myName.Yr],data.import[,ContData.env$myName.Mo]))
        print(knitr::kable(myTable, format="markdown", row.names=TRUE))
    cat("\n\n")

    
  # revert to longer table (20170228)
    cat("Number of records by day and month (with totals).")
    cat("\n")
    myTable <- addmargins(table(data.import[,ContData.env$myName.Day],data.import[,ContData.env$myName.Mo]))
        print(knitr::kable(myTable, format="markdown", row.names=TRUE))
    cat("\n\n") 

#     
#     pandoc.table(myTable.month.day.rec.GT15,style="rmarkdown")
#    
#     
    myTable.month.day.rec <- table(data.import[,ContData.env$myName.Mo],data.import[,ContData.env$myName.Day])
#     use apply function to count number of records not equal to the expected value
    cat("\n\n")
    

    #
    myTable.DateTime.N <- aggregate(data.import[,ContData.env$myName.SiteID]  
                                    ~ data.import[,ContData.env$myName.DateTime]
                                    , data=data.import,FUN=length)
    # myTable <- myTable.DateTime.N[myTable.DateTime.N[,ContData.env$myName.SiteID]!=1,]
    # cat(paste0("Date and time records with more than one entry; N=",nrow(myTable),". Duplicate date.time records are shown below."))
    # cat("\n")
    #   print(knitr::kable(myTable, format="markdown", row.names=TRUE))
    # mask error, 20170307
    
    # Missing Dates
    
    myDateRange.Data <- seq(as.Date(min(data.import[,ContData.env$myName.Date]))
                            ,as.Date(max(data.import[,ContData.env$myName.Date]))
                            ,by="day")
    
    if(exists("fun.myData.DateRange.Start")==TRUE){
      myDateRange.Target <- seq(as.Date(fun.myData.DateRange.Start)
                              ,as.Date(fun.myData.DateRange.End)
                              ,by="day")
    } else {
      myDateRange.Target <- myDateRange.Data
    }
    
    myDateRange.Target.Missing <- myDateRange.Target[!myDateRange.Target %in% myDateRange.Data]
    cat(paste0("Below are the dates with missing data between the min (",min(myDateRange.Data)
               ,") and max(",max(myDateRange.Data)," for the provided data. There are "
               ,length(myDateRange.Target.Missing)," records."))
    cat("\n\n")
    print(ifelse(length(myDateRange.Target.Missing)==0,"",myDateRange.Target.Missing))

```


# FLAGS, OVERALL, BY PARAMETER
Flags are assigned to each data point (a single measured parameter at a unique point in time) first by each of the QC tests below.  Flags are assigned numerical values;

```{r flags_legend, results='asis', echo=FALSE, warning=FALSE}
cat(paste("* **",ContData.env$myFlagVal.Pass,"** = Pass,",sep=""))
cat("\n")
cat(paste("* **",ContData.env$myFlagVal.Suspect,"** = Suspect,",sep=""))  
cat("\n")
cat(paste("* **",ContData.env$myFlagVal.Fail,"** = Fail,",sep=""))
cat("\n")
cat(paste("* **",ContData.env$myFlagVal.NoData,"** = No Data or Not Applicable (NA).",sep=""))
```

Overall flags are assigned by examining the results of the four tests below. 

```{r flags_overall, results='asis', echo=FALSE, warning=FALSE}
cat(paste("* **",ContData.env$myFlagVal.Pass,"** = no Fail or Suspect and at least one Pass,",sep=""))
cat("\n")
cat(paste("* **",ContData.env$myFlagVal.Suspect,"** = no Fail and at least one Suspect,",sep="")) 
cat("\n") 
cat(paste("* **",ContData.env$myFlagVal.Fail,"** = at least one Fail,",sep=""))
cat("\n")
cat(paste("* **",ContData.env$myFlagVal.NoData,"** = all tests were Missing Data.",sep=""))
```

Overall flags by parameter

```{r flags_parameters, results='asis', echo=FALSE, warning=FALSE}
#
     for (j in 1:length(myParameters)) {##FOR.j.START
#       #
       #j.num <- match(j,myParameters)
 #   cat(paste(myParameters.Lab[j.num],"/n/n",sep=""))
       
       # ISSUE WITH knitr::kable INSIDE OF LOOPS
       
    cat(paste("## ",myParameters[j],"\n\n",sep=""))

       colnum <- match(paste("Flag",myParameters[j],sep="."),names(data.import))
       
       #print(myTable.Flags.Overall <- ftable(data.import[,colnum]))
       myTable <- addmargins(table(data.import[,colnum]),1)
       print(knitr::kable(t(as.matrix(myTable)), format = "markdown"))
       # future mod, 1,3,4,9 to Pass, Suspect, Fail, NA
       # exclude=NA to get all
       # future mod, 2nd line in table to include Percent of row total
       # future mod, sort levels
       
       cat("\n\n")
       
#       #
     }##FOR.j.END
```

# QC TESTS, BY PARAMETER
* **Gross Range Test (Gross):** Test if data point exceeds sensor or user defined min/max.  The values are user defined based on parameter being measured and measuring instrument.
* **Spike Test (Spike):** Test if data point exceeds a user defined threshold relative to the previous data point.  The user defined values are based on the parameter being measured.
* **Rate of Change Test (RoC):** Test if a data point exceeds a number of standard deviations from the previous data points over a user defined time period.  Default is a 25 hour time period and 3 standard deviations.
* **Flat Line Test (Flat):** Test if a data point is within a user defined threshold from previous data points over a user defined range.  Default is 3 previous points for suspect and 5 points for failure.  The threshold is user defined and based on the measured parameter and sensitivity of the measuring instrument.


```{r qc_tests_parameters, results='asis', echo=FALSE, warning=FALSE}
 # 3. Data Info, by Parameter
    # Individual Data Type Report
    # QC
    #i <- myParameters[1]

     for (i in myParameters) {##FOR.i.START
#       #
       i.num <- match(i,myParameters)
       myTitle.Sub <- myParameters.Lab[i.num]
       
       
      cat("## QC TESTS, ",i,"\n\n",sep="")
       
       #cat(paste("**QC TESTS,",myTitle.Sub,sep=""))
       
       # 3.1. Flags, overall
       cat(myTitle.Sub <- "### Flags")
             cat("\n\n")
      cat("#### Flag summary, overall number of records.")
      cat("\n\n")
       myTable <- addmargins(table(data.import[,paste("Flag",i,sep=".")]),1)
       print(knitr::kable(t(as.matrix(myTable)), format = "markdown"))
      
      cat("\n\n")
       
      #
      # 3.1. Number of Records (revised 20170228)
       # Convert time interval (minutes) to number per day
      records.expected <- round(24*60/as.numeric(myTimeDiff[1]),1)
      cat(paste("Estimated number of records per day is ",records.expected,".",sep=""))
      cat("\n\n")
      #
      cat("Number of records by year and month (with totals)")
      cat("\n")
      myTable <- addmargins(table(data.import[,ContData.env$myName.Yr],data.import[,ContData.env$myName.Mo]))
      print(knitr::kable(myTable, format="markdown", row.names=TRUE))
      cat("\n\n")
      #
      cat("Number of records by day and month (with totals)")
      cat("\n")
      myTable <- addmargins(table(data.import[,ContData.env$myName.Day],data.import[,ContData.env$myName.Mo]))
      print(knitr::kable(myTable, format="markdown", row.names=TRUE))
      cat("\n\n") 
      #
      # identify days/months where not the expected number of records
      # (expect first and last day)
  #    print("days where not the expected number of records")
      #
      # 3.2. Flags by QC Test
      
      cat("\n\n")
      
      cat("#### Flags by QC Test")
      
      cat("\n\n")
      
      cat("##### Flags, Gross\n\n")
      
      myTable <- addmargins(table(data.import[,paste(ContData.env$myName.Flag,"Gross",i,sep=".")]),1)
      print(knitr::kable(t(as.matrix(myTable)), format = "markdown"))
        cat("\n\n")
      cat("##### Flags, Spike\n\n")
      
      myTable <- addmargins(table(data.import[,paste(ContData.env$myName.Flag,"Spike",i,sep=".")]),1)
      print(knitr::kable(t(as.matrix(myTable)), format = "markdown"))
        cat("\n\n")
      cat("##### Flags, RoC\n\n")
      
      myTable <- addmargins(table(data.import[,paste(ContData.env$myName.Flag,"RoC",i,sep=".")]),1)
      print(knitr::kable(t(as.matrix(myTable)), format = "markdown"))
        cat("\n\n")
      cat("##### Flags, Flat\n\n")
      
      myTable <- addmargins(table(data.import[,paste(ContData.env$myName.Flag,"Flat",i,sep=".")]),1)
      print(knitr::kable(t(as.matrix(myTable)), format = "markdown"))
        cat("\n\n")
      cat("QC Test Flag fields are saved in the data file so the user can identify data points that have been flagged as suspect or fail.")
     
      #
      #myFlagTests <- c("Gross","Spike","RoC","Flat")
      #(myTable.Flags.Flat <- ftable(data.import[,paste("Flag",myFlagTests,i,sep=".")]))
      #
      
      
      cat(paste("\n\n Test results marked as ",ContData.env$myFlagVal.NoData," (No/Missing Data) if unable to calculate the end point needed for the test.  For example, the first record does not have a previous record for comparison for the Gross QC Test.  QC Test flags are saved in the data file.",sep=""))
      
      #
      # 3.3. Plot
      data.plot <- data.import
      #
      # cheat on Date/Time axis
      n.Total <- length(data.plot[,ContData.env$myName.Date])
      pct <- c(20,40,60,80,100)*.01
      myAT <- c(1,round(n.Total * pct,0))
      myLab <- data.plot[,ContData.env$myName.Date][myAT]
      #
      myPlot.Y <- na.omit(as.numeric(data.plot[,i])) #20170518, v2.0.1.9008, coming in as text add na.omit(as.numeric(x))
      myPlot.Ylab <- myParameters.Lab[i.num]
      plot(myPlot.Y,type="l",main=mySiteID,xlab=ContData.env$myLab.Date,ylab=myPlot.Ylab,col="gray", xaxt="n")
      axis(1,at=myAT,labels=myLab,tick=TRUE)
      # Add discrete (only if present)
      myDiscrete <- paste(ContData.env$myPrefix.Discrete,i,sep=".")
      if (myDiscrete %in% myParameters.ALL == TRUE){##IF.Discrete.START
        data.plot[,myDiscrete] <- as.numeric(data.plot[,myDiscrete]) # coerce "NA" to NA
        data.plot.points <- na.omit(data.plot[,c(ContData.env$myName.DateTime,myDiscrete)]) # remove NA
        myPoints.X <- as.numeric(rownames(data.plot.points))
        myPoints.Y <- data.plot.points[,myDiscrete]
        points(myPoints.Y~myPoints.X,col="black",pch=19) 
      }##IF.Discrete.END
      cat("\n\n")
      cat("Discrete measurements, if any, show up as points on the plot.")
      cat("\n\n")
      
      #
    }##FOR.i.END

```

# PLOTS, MULTIPARAMETER
Multiparameter plots if exist in the data.

```{r plots, results='asis', echo=FALSE, warning=FALSE}
 # BOTH plots
    
    # 3.3. Plot
    data.plot <- data.import
    #
    # cheat on Date/Time axis
    n.Total <- length(data.plot[,ContData.env$myName.Date])
    pct <- c(20,40,60,80,100)*.01
    myAT <- c(1,round(n.Total * pct,0))
    myLab <- data.plot[,ContData.env$myName.Date][myAT]
    #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
    # Need to check for parameters before plot
    #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ 
    
    # Temp, Air vs. Water
    if (ContData.env$myName.AirTemp %in% myParameters & ContData.env$myName.WaterTemp 
        %in% myParameters == TRUE){##IF.Temp.START
      cat("## PLOT, Temperature (Air vs. Water) \n\n" )
      #
      par.orig <- par(no.readonly=TRUE) # save original par settings
      layout(rbind(1,2),heights=c(7,1))
      #
      myPlot.Y <- na.omit(as.numeric(data.plot[,ContData.env$myName.AirTemp])) # 20170518, v2.0.1.9008
      myPlot.Y2 <- na.omit(as.numeric(data.plot[,ContData.env$myName.WaterTemp])) # 20170518, v2.0.1.9008
      myPlot.Ylab <- ContData.env$myLab.Temp.BOTH
      plot(myPlot.Y,type="l",main=mySiteID,xlab=ContData.env$myLab.Date,ylab=myPlot.Ylab,col="green", xaxt="n")
      # Revised myAT for lots of NA (20170518)
      data.length <- length(myPlot.Y)
      myAT <- c(1,round(data.length * pct,0))
      #
      axis(1,at=myAT,labels=myLab,tick=TRUE)
      lines(myPlot.Y2,type="l",col="blue")
      #legend(x="bottomright",lty=1,col=c("green","blue"),legend=c("air","water"))
      # Add discrete, AirTemp (only if present)
      myDiscrete <- paste(ContData.env$myPrefix.Discrete,ContData.env$myName.AirTemp,sep=".")
      if (myDiscrete %in% myParameters.ALL == TRUE){##IF.Discrete.START
        data.plot[,myDiscrete] <- as.numeric(data.plot[,myDiscrete]) # coerce "NA" to NA
        data.plot.points <- na.omit(data.plot[,c(ContData.env$myName.DateTime,myDiscrete)]) # remove NA
        myPoints.X <- as.numeric(rownames(data.plot.points))
        myPoints.Y <- data.plot.points[,myDiscrete]
        points(myPoints.Y~myPoints.X,col="green",pch=19) 
      }##IF.Discrete.END
      # Add discrete, Water.Temp (only if present)
      myDiscrete <- paste(ContData.env$myPrefix.Discrete,ContData.env$myName.WaterTemp,sep=".")
      if (myDiscrete %in% myParameters.ALL == TRUE){##IF.Discrete.START
        data.plot[,myDiscrete] <- as.numeric(data.plot[,myDiscrete]) # coerce "NA" to NA
        data.plot.points <- na.omit(data.plot[,c(ContData.env$myName.DateTime,myDiscrete)]) # remove NA
        myPoints.X <- as.numeric(rownames(data.plot.points))
        myPoints.Y <- data.plot.points[,myDiscrete]
        points(myPoints.Y~myPoints.X,col="blue",pch=19) 
      }##IF.Discrete.END
      #
      # LEGEND
      par(mar=c(0,0,0,0))
      plot.new()
      legend(x="center",lty=1,col=c("green","blue"),legend=c("air","water"),bty="n")
      #
      par(par.orig) # return to original par settings
      #
      # Future mod, add points to legend
      cat("\n\n")
      cat("Discrete measurements, if any, show up as points on the plot.")
      cat("\n\n")

      #
    }##IF.Temp.END
    #
    # Water, Temp vs Level
    if (ContData.env$myName.WaterTemp %in% myParameters & ContData.env$myName.SensorDepth 
        %in% myParameters == TRUE){##IF.Temp_Level.START
      cat("## PLOT, Sensor Depth vs. Water Temperature \n\n")
      #
      par.orig <- par(no.readonly=TRUE) # save original par settings
      layout(rbind(1,2),heights=c(7,1))
      par(oma=c(0,0,0,2))
      #
      myPlot.Y <- na.omit(as.numeric(data.plot[,ContData.env$myName.WaterTemp])) # 20170518, v2.0.1.9008
      myPlot.Ylab <- ContData.env$myLab.WaterTemp
      myPlot.Y2 <- na.omit(as.numeric(data.plot[,ContData.env$myName.SensorDepth])) # 20170518, v2.0.1.9008
      myPlot.Y2lab <- ContData.env$myLab.SensorDepth
      #
      plot(myPlot.Y,type="l",main=mySiteID,xlab=ContData.env$myLab.Date,ylab=myPlot.Ylab,col="blue", xaxt="n")
      # Revised myAT for lots of NA (20170518)
      data.length <- length(myPlot.Y)
      myAT <- c(1,round(data.length * pct,0))
      #
      axis(1,at=myAT,labels=myLab,tick=TRUE)
      # Add discrete, Water.Temp (only if present)
      myDiscrete <- paste(ContData.env$myPrefix.Discrete,ContData.env$myName.WaterTemp,sep=".")
      if (myDiscrete %in% myParameters.ALL == TRUE){##IF.Discrete.START
        data.plot[,myDiscrete] <- as.numeric(data.plot[,myDiscrete]) # coerce "NA" to NA
        data.plot.points <- na.omit(data.plot[,c(ContData.env$myName.DateTime,myDiscrete)]) # remove NA
        myPoints.X <- as.numeric(rownames(data.plot.points))
        myPoints.Y <- data.plot.points[,myDiscrete]
        points(myPoints.Y~myPoints.X,col="blue",pch=19) 
      }##IF.Discrete.END
      #
      # Add 2nd y axis (2nd color is black)
      par(new=TRUE)
      plot(myPlot.Y2,type="l",col="black",axes=FALSE,ann=FALSE)
      axis(4)
      mtext(myPlot.Y2lab,side=4,line=2.5)
      # Add discrete, SensorDepth (only if present)
      myDiscrete <- paste(ContData.env$myPrefix.Discrete,ContData.env$myName.SensorDepth,sep=".")
      if (myDiscrete %in% myParameters.ALL == TRUE){##IF.Discrete.START
        data.plot[,myDiscrete] <- as.numeric(data.plot[,myDiscrete]) # coerce "NA" to NA
        data.plot.points <- na.omit(data.plot[,c(ContData.env$myName.DateTime,myDiscrete)]) # remove NA
        myPoints.X <- as.numeric(rownames(data.plot.points))
        myPoints.Y <- data.plot.points[,myDiscrete]
        points(myPoints.Y~myPoints.X,col="black",pch=19) 
      }##IF.Discrete.END
      #
      # LEGEND
      par(mar=c(0,0,0,0))
      plot.new()
      legend(x="center",lty=1,col=c("blue","black"),legend=c("temperature","sensor depth"),bty="n")
    #
      # Future mod, add points to legend
      #
    par(par.orig) # return to original par settings
    cat("\n\n")
    cat("Discrete measurements, if any, show up as points on the plot.")
    cat("\n\n")
  }##IF.Temp_Level.END
    
   # '''
```

